---
title: "0_All_Immune Gene_Curation"
author: "Ursula Widocki"
date: "7/6/2021"
output: html_document
---

#########################################################################################
# 
# This file gets all of the genes from GO, KEGG, InnateDB, and ReactomeDB associated with 
# the immune system and distinguishes between what each db defines as the innate
# immune system, adaptive immune system, and other components of immunity
# 
# Makes one database-like file of gene, immune pathway, and db information
#
#########################################################################################

```{r setup, include=FALSE}
rm(list=ls())
```

```{r}
# Packages and Libraries
library(tidyverse)
library(dplyr)
library(data.table)
library(igraph)
`%ni%` <- Negate(`%in%`)

# where the Entrez to gene symbol conversion is coming from
gene_human <- fread("/Users/ursulawidocki/Desktop/BarabasiLab/Data/gene_human.csv")
gene_human <- gene_human[,2:3]
```

```{r}
# Read in PPI
ncppi <- fread('/Users/ursulawidocki/Desktop/BarabasiLab/Data/ncPPI_PPI_2022_04042022.csv')
ncppi_df <- ncppi[,c("HGNC_Symbol.1", "HGNC_Symbol.2")]

ncppi_df = ncppi_df[!(!is.na(ncppi_df$HGNC_Symbol.2) & ncppi_df$HGNC_Symbol.2 ==""), ]
ncppi_df = ncppi_df[!(!is.na(ncppi_df$HGNC_Symbol.1) & ncppi_df$HGNC_Symbol.1 ==""), ]

ncppi_df$value = 1
ncppi_df = ncppi_df %>% unique()
ncppi_g <- igraph::graph_from_data_frame(ncppi_df, directed = F)
ncppi_g <- simplify(ncppi_g)

ncppi_degree_df = data.frame(Degree = igraph::degree(graph = ncppi_g)) %>%
  mutate(Gene = row.names(.))
```


### GO
```{r}
# for GO
library(GO.db)
# where the GO data is coming from
gene2go <- fread(file = "/Users/ursulawidocki/Desktop/BarabasiLab/Data/gene2go")
evid = c("EXP", "IDA", "IPI", "IMP", "IGI", "IEP", "HTP", "HDA", "HMP", "HGI", "HEP", "IBA", "IBD", "IKR", "IRD")
#bad_evid = c("NAS", "ND", "IEA", "ISS", "IC") # http://geneontology.org/docs/guide-go-evidence-codes/
gene2go = gene2go %>%
  filter(`#tax_id` == 9606) %>%
  filter(Evidence %in% evid)
  #filter(Evidence %ni% bad_evid)
```

### GO
# Gets all innate immune response genes
```{r}
go_id = GOID( GOTERM[ Term(GOTERM) == "innate immune response"]) # all GO IDs for innate immune 

# OFFSPRING consists of children of GO terms and all of their offspring
innate_offspring <- as.list(GOBPOFFSPRING)
innate_offspring <- innate_offspring[!is.na(innate_offspring)]

innate_offspring = c(go_id, innate_offspring$`GO:0045087`) # all child paths of innate immune response

# Get genes in paths based on gene2go
go_innate_df = gene2go %>% 
  filter(GO_ID %in% innate_offspring)

# use the human gene symbol file to convert from Entrez to symbol
go_innate_df = merge(go_innate_df, gene_human)

go_innate_df = go_innate_df[,c("Symbol", "GO_ID", "GO_term")] # pick cols we want
colnames(go_innate_df) = c("Symbol", "GOPathIDInnate", "GOPathwayInnate") # rename cols
go_innate_df$GO <- 1
go_innate_df$isInnateGO <- 1

```

# Gets all adaptive immune response genes
```{r}
go_id = GOID( GOTERM[ Term(GOTERM) == "adaptive immune response"]) # all GO IDs for innate immune 

# OFFSPRING consists of children of GO terms and all of their
adapt_offspring <- as.list(GOBPOFFSPRING)
adapt_offspring <- adapt_offspring[!is.na(adapt_offspring)]

adapt_offspring = c(go_id, adapt_offspring$`GO:0002250`) # all child paths of innate immune response

# Get genes in paths based on gene2go

go_adapt_df = gene2go %>% 
  filter(GO_ID %in% adapt_offspring)

# use the human gene symbol file to convert from Entrez to symbol
go_adapt_df = merge(go_adapt_df, gene_human)

go_adapt_df = go_adapt_df[,c("Symbol", "GO_ID", "GO_term")] # pick cols we want
colnames(go_adapt_df) = c("Symbol", "GOPathIDAdaptive", "GOPathwayAdaptive") # rename cols
go_adapt_df$GO <- 1
go_adapt_df$isAdaptiveGO <- 1

```

# Gets all GO immune response genes in paths not in innate or adaptive
```{r}
# get all paths under immune root

go_id = GOID( GOTERM[ Term(GOTERM) == "immune response"])

# OFFSPRING consists of children of GO terms and all of their
offspring <- as.list(GOBPOFFSPRING)
offspring <- offspring[!is.na(offspring)]

offspring = c(go_id, offspring$`GO:0006955`) # all child paths of innate immune response
offspring = offspring[offspring %ni% innate_offspring]
offspring = offspring[offspring %ni% adapt_offspring]

# Get genes in paths based on gene2go

go_other_df = gene2go %>% 
  filter(GO_ID %in% offspring)

# use the human gene symbol file to convert from Entrez to symbol
go_other_df = merge(go_other_df, gene_human)

go_other_df = go_other_df[,c("Symbol", "GO_ID", "GO_term")] # pick cols we want
colnames(go_other_df) = c("Symbol", "GOPathIDOther", "GOPathwayOther") # rename cols
go_other_df$GO <- 1
go_other_df$isOtherGO <- 1

```






### KEGG
```{r}
# for KEGG
library(KEGGREST)
database = "pathway"
```

# Gets innate immunity genes
```{r}
innate_KEGG_paths <- c("hsa04062", "hsa04610",
                       "hsa04611", "hsa04612", 
                       "hsa04613", "hsa04620", 
                       "hsa04621", "hsa04622", 
                       "hsa04623", "hsa04625", 
                       "hsa04640", "hsa04650", 
                       "hsa04657", "hsa04664", 
                       "hsa04670", "hsa04672")

# keggGet can only get 10 inputs due to server limitations
query1 <- keggGet(innate_KEGG_paths[1:10])

query2 <-keggGet(innate_KEGG_paths[11:length(innate_KEGG_paths)])

col_labels <- c("Symbol", "KEGG", "KEGGPathIDInnate", "KEGGPathwayInnate")
kegg_innate_df <- data.frame(matrix(ncol = length(col_labels), nrow = 0))
colnames(kegg_innate_df) <- col_labels

for(p in 1:length(query1)){ # for each path in the query
  pathname = query1[[p]]$NAME # get path name
  pathID = query1[[p]]$ENTRY # get path id
  
  pathgenes = query1[[p]]$GENE # gets list of genes in query p
  
  # to extract EntrezID
  gene = pathgenes[seq(1,length(pathgenes), 2)]
  
  for(g in gene){ # for each gene, add line of its pathway and info
    symb_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
    new_line <- c(symb_gene, "1", pathID, pathname)
    kegg_innate_df[nrow(kegg_innate_df)+1,] <- new_line
  }
}

for(p in 1:length(query2)){
  pathname = query2[[p]]$NAME # get path name
  pathID = query2[[p]]$ENTRY # get path id
  
  pathgenes = query2[[p]]$GENE # gets list of genes in query p
  
  # to extract EntrezID
  gene = pathgenes[seq(1,length(pathgenes), 2)]
  
  for(g in gene){ # for each gene, add line of its pathway and info
    symb_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
    new_line <- c(symb_gene, 1, pathID, pathname)
    kegg_innate_df[nrow(kegg_innate_df)+1,] <- new_line
    
  }
}

kegg_innate_df$isInnateKEGG <- 1

```

# Get adaptive immunity genes
```{r}
adapt_KEGG_paths <- c("hsa04062", "hsa04610", 
                      "hsa04612", "hsa04640", 
                      "hsa04657", "hsa04658", 
                      "hsa04659", "hsa04660", 
                      "hsa04662", "hsa04664", 
                      "hsa04666", "hsa04670", 
                      "hsa04672")

# keggGet can only get 10 inputs due to server limitations
query1 <- keggGet(adapt_KEGG_paths[1:10])

query2 <-keggGet(adapt_KEGG_paths[11:length(adapt_KEGG_paths)])

col_labels <- c("Symbol", "KEGG", "KEGGPathIDAdaptive", "KEGGPathwayAdaptive")
kegg_adapt_df <- data.frame(matrix(ncol = length(col_labels), nrow = 0))
colnames(kegg_adapt_df) <- col_labels

for(p in 1:length(query1)){
  pathname = query1[[p]]$NAME # get path name
  pathID = query1[[p]]$ENTRY # get path id
  
  pathgenes = query1[[p]]$GENE # gets list of genes in query p
  
  # to extract EntrezID
  gene = pathgenes[seq(1,length(pathgenes), 2)]
  
  for(g in gene){ # for each gene, add line of its pathway and info
    symb_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
    new_line <- c(symb_gene, "1", pathID, pathname)
    kegg_adapt_df[nrow(kegg_adapt_df)+1,] <- new_line
  }
}

for(p in 1:length(query2)){
  pathname = query2[[p]]$NAME # get path name
  pathID = query2[[p]]$ENTRY # get path id
  
  pathgenes = query2[[p]]$GENE # gets list of genes in query p
  
  # to extract EntrezID
  gene = pathgenes[seq(1,length(pathgenes), 2)]
  
  for(g in gene){ # for each gene, add line of its pathway and info
    symb_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
    new_line <- c(symb_gene, 1, pathID, pathname)
    kegg_adapt_df[nrow(kegg_adapt_df)+1,] <- new_line
  }
}

kegg_adapt_df$isAdaptiveKEGG <- 1

```



### InnateDB
The website can be found here: https://www.innatedb.com

The page where we downloaded the data can be found here: https://www.innatedb.com/annotatedGenes.do?type=innatedb 

```{r}
# for InnateDB
library(readxl)
# From https://www.innatedb.com/annotatedGenes.do?type=innatedb
man_file <- "/Users/ursulawidocki/Desktop/BarabasiLab/Data/innatedb_curated_genes_innate_immunity.xls"
innatedb_df <- read_xls(man_file)

# alias conversion is necessary if gene symbol is not found in gene_human["Symbol"]
#alias_dict = fread("/Users/ursulawidocki/Desktop/BarabasiLab/Data/GeneSymbolToAliasANDPreviousNames.txt", 
#                        sep = "\t", stringsAsFactors = F, header = T) 


symbol_dict <- fread("/Users/ursulawidocki/Desktop/BarabasiLab/Data/multiple_hgnc_dict_set_2022-04-04.txt")
```

```{r}
innatedb_df = innatedb_df %>%
  filter(Species == "9606")
innatedb_df <- innatedb_df[,c("Gene Symbol", "Annotation")]
innatedb_df$upper <- toupper(innatedb_df$`Gene Symbol`) # potential protein symbols converted to gene symbols
innatedb_df$InnateDB <- 1
```

```{r}
# get indices of upper not in Symbol and get corresponding Gene Symbol
odd_gene_ind <- which(innatedb_df$upper %ni% symbol_dict$HGNC_Symbol)
odd_gene <- innatedb_df$`Gene Symbol`[odd_gene_ind]

good_genes_df <- innatedb_df %>%
  filter(upper %in% symbol_dict$HGNC_Symbol) %>%
  dplyr::select(-`Gene Symbol`)
colnames(good_genes_df)[2] <- "Symbol"

bad_genes_df <- innatedb_df[odd_gene_ind,] %>% dplyr::select(-upper)
colnames(bad_genes_df)[1] <- "alias"
# get gene symbols of bad genes that are aliases
bad_genes_df <- left_join(bad_genes_df, symbol_dict)
bad_genes_df <- bad_genes_df %>% 
  dplyr::select(-alias) %>%
  drop_na(HGNC_Symbol)
colnames(bad_genes_df)[3] <- "Symbol"
bad_genes_df <- bad_genes_df[,c("Annotation", "Symbol", "InnateDB")]

# merge with good_genes_df
innatedb_df <- rbind(good_genes_df, bad_genes_df)
innatedb_df$isInnateInnateDB <- 1
colnames(innatedb_df)[1] <- "InnateDBPathway"

```



### ReactomeDB

```{r}
library(reactome.db)
reactomeIDs <- reactomePATHNAME2ID # maps Reactome path identifiers to reactomeIDs
entrezGenes <- reactomePATHID2EXTID # maps reactome IDs to Entrez gene names
entrez_to_ID <- reactomeEXTID2PATHID
path_ID_to_name <- reactomePATHID2NAME
go_to_reactome <- reactomeGO2REACTOMEID
```

```{r}
# use GO innate: GO:0045087

xx <- c(unique(as.list(reactomeGO2REACTOMEID$`GO:0045087`)))
#reactome_innate_path <- c(as.list(reactomePATHID2NAME$`R-HSA-168249`)) # pathway name
ID <- xx[[1]]
reactome_innate_genes <- entrezGenes[[ID]]

# set up df to store genes and paths
col_labels <- c("Symbol", "ReactomePathwayInnate", "ReactomePathIDInnate", "ReactomeDB")
reactome_innate_df <- data.frame(matrix(ncol = length(col_labels), nrow = 0))
colnames(reactome_innate_df) <- col_labels

for(g in reactome_innate_genes){
    if(g %in% gene_human$GeneID){
      sym_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
      name_path <- path_ID_to_name[[ID]]
      new_line <- c(sym_gene, name_path, ID, 1)
      reactome_innate_df[nrow(reactome_innate_df) + 1,] <- new_line
      
    }
}

reactome_innate_df$isInnateReactome <- 1

```

```{r}
# use GO adaptive: GO:0002250

xx <- c(unique(as.list(reactomeGO2REACTOMEID$`GO:0002250`)))
ID <- xx[[1]]
reactome_adaptive_genes <- entrezGenes[[ID]]

# set up df to store genes and paths
col_labels <- c("Symbol", "ReactomePathwayAdaptive", "ReactomePathIDAdaptive", "ReactomeDB")
reactome_adapt_df <- data.frame(matrix(ncol = length(col_labels), nrow = 0))
colnames(reactome_adapt_df) <- col_labels

for(g in reactome_adaptive_genes){
    if(g %in% gene_human$GeneID){
      sym_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
      name_path <- path_ID_to_name[[ID]]
      new_line <- c(sym_gene, name_path, ID, 1)
      reactome_adapt_df[nrow(reactome_adapt_df) + 1,] <- new_line
      
    }
}

reactome_adapt_df$isAdaptiveReactome = 1
```




### Bring together all databases

```{r}
full_join_g = plyr::join_all(list(go_innate_df, go_adapt_df, go_other_df), type = "full")
full_join_k = plyr::join_all(list(kegg_innate_df, kegg_adapt_df), type = "full")
full_join_r = plyr::join_all(list(reactome_innate_df, reactome_adapt_df), type = "full")
full_join = plyr::join_all(list(full_join_g, full_join_k, full_join_r, innatedb_df), type = "full")

full_join$isInnateGO[is.na(full_join$isInnateGO)] = 0
full_join$isInnateKEGG[is.na(full_join$isInnateKEGG)] = 0
full_join$isInnateInnateDB[is.na(full_join$isInnateInnateDB)] = 0
full_join$isInnateReactome[is.na(full_join$isInnateReactome)] = 0

full_join$isAdaptiveGO[is.na(full_join$isAdaptiveGO)] = 0
full_join$isAdaptiveKEGG[is.na(full_join$isAdaptiveKEGG)] = 0
full_join$isAdaptiveReactome[is.na(full_join$isAdaptiveReactome)] = 0

full_join$isOtherGO[is.na(full_join$isOtherGO)] = 0

full_join$GO[is.na(full_join$GO)] = 0
full_join$InnateDB[is.na(full_join$InnateDB)] = 0
full_join$KEGG[is.na(full_join$KEGG)] = 0
full_join$ReactomeDB[is.na(full_join$ReactomeDB)] = 0

# filter for proteins in ppi
full_join <- full_join %>% filter(Symbol %in% V(ncppi_g)$name) %>% unique()
```

```{r}
write.table(full_join, "/Users/ursulawidocki/Desktop/BarabasiLab/Data/immunity_genes_all_noncoding.tsv", sep = "\t", row.names = T, col.names = T)
```



# look at full_join to make sure it can still give expected results
```{r}
temp <- full_join %>% 
  dplyr::select(Symbol, InnateDB) %>%
  filter(InnateDB == 1)
length(unique(temp$Symbol))

# number of pathways in InnateDB
length(unique(c(full_join$InnateDBPathway)))
```






######################################################################
# Code I am not using

### ReactomeDB
#```{r}
# for ReactomeDB
library(reactome.db)
reactomeIDs <- reactomePATHNAME2ID # maps Reactome path identifiers to reactomeIDs
entrezGenes <- reactomePATHID2EXTID # maps reactome IDs to Entrez gene names
entrez_to_ID <- reactomeEXTID2PATHID
path_ID_to_name <- reactomePATHID2NAME
#```


## Get innate immunity genes from ReactomeDB
#```{r}
## List of all pathways I need

innate_paths <- c("Homo sapiens: Innate Immune System",
                  "Homo sapiens: Toll-like Receptor Cascades", 
                  "Homo sapiens: Complement cascade", 
                  "Homo sapiens: Nucleotide-binding domain, leucine rich repeat containing receptor (NLR) signaling pathways", 
                  "Homo sapiens: Advanced glycosylation endproduct receptor signaling",
                  "Homo sapiens: DDX58/IFIH1-mediated induction of interferon-alpha/beta",
                  "Homo sapiens: Cytosolic sensors of pathogen-associated DNA ", 
                  "Homo sapiens: Fcgamma receptor (FCGR) dependent phagocytosis", 
                  "Homo sapiens: DAP12 interactions", 
                  "Homo sapiens: Fc epsilon receptor (FCERI) signaling", 
                  "Homo sapiens: C-type lectin receptors (CLRs)", 
                  "Homo sapiens: Antimicrobial peptides", 
                  "Homo sapiens: Neutrophil degranulation", 
                  "Homo sapiens: ROS and RNS production in phagocytes", 
                  "Homo sapiens: Alpha-protein kinase 1 signaling pathway", 
                  
                  "Homo sapiens: Cytokine Signaling in Immune system",
                  "Homo sapiens: Interferon Signaling", 
                  "Homo sapiens: Signaling by Interleukins",
                  "Homo sapiens: Growth hormone receptor signaling",
                  "Homo sapiens: Prolactin receptor signaling", 
                  "Homo sapiens: TNFR2 non-canonical NF-kB pathway", 
                  "Homo sapiens: FLT3 Signaling", 
                  "Homo sapiens: Signaling by CSF3 (G-CSF)")

# Get all Reactome IDs for all of the paths
path_IDs <- c()
for (path in innate_paths){
  path_IDs <- append(path_IDs, reactomeIDs[[path]])
  
}

# set up df to store genes and paths
col_labels <- c("Symbol", "ReactomePathwayInnate", "ReactomePathIDInnate", "ReactomeDB")
reactome_innate_df <- data.frame(matrix(ncol = length(col_labels), nrow = 0))
colnames(reactome_innate_df) <- col_labels

for (ID in path_IDs){
  reactome_genes = entrezGenes[[ID]] # gets all Entrez genes in paths
  
  for(g in reactome_genes){
    if(g %in% gene_human$GeneID){
      sym_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
      name_path <- path_ID_to_name[[ID]]
      new_line <- c(sym_gene, name_path, ID, "1")
      reactome_innate_df[nrow(reactome_innate_df) + 1,] <- new_line
      
    }
  }
}

reactome_innate_df$isInnateReactome = 1

#```

## Get adaptive immunity genes in ReactomeDB
#```{r}
## List of all pathways I need

adapt_paths <- c("Homo sapiens: Adaptive Immune System",
                 "Homo sapiens: TCR signaling",
                 "Homo sapiens: Costimulation by the CD28 family",
                 "Homo sapiens: Signaling by the B Cell Receptor (BCR)",
                 "Homo sapiens: Class I MHC mediated antigen processing & presentation",
                 "Homo sapiens: MHC class II antigen presentation",
                 "Homo sapiens: Immunoregulatory interactions between a Lymphoid and a non-Lymphoid cell",
                 "Homo sapiens: Rap1 signaling",
                 "Homo sapiens: Butyrophilin (BTN) family interactions", 
                 
                 "Homo sapiens: Cytokine Signaling in Immune system",
                 "Homo sapiens: Interferon Signaling", 
                 "Homo sapiens: Signaling by Interleukins",
                 "Homo sapiens: Growth hormone receptor signaling",
                 "Homo sapiens: Prolactin receptor signaling", 
                 "Homo sapiens: TNFR2 non-canonical NF-kB pathway", 
                 "Homo sapiens: FLT3 Signaling", 
                 "Homo sapiens: Signaling by CSF3 (G-CSF)")

# Get all Reactome IDs for all of the paths
path_IDs <- c()
for (path in adapt_paths){
  path_IDs <- append(path_IDs, reactomeIDs[[path]])
  
}

# set up df to store genes and paths
col_labels <- c("Symbol", "ReactomePathwayAdaptive", "ReactomePathIDAdaptive", "ReactomeDB")
reactome_adapt_df <- data.frame(matrix(ncol = length(col_labels), nrow = 0))
colnames(reactome_adapt_df) <- col_labels

for (ID in path_IDs){
  
  reactome_genes = entrezGenes[[ID]] # gets all Entrez genes in paths
  
  for(g in reactome_genes){
    
    if(g %in% gene_human$GeneID){
      sym_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
      name_path <- path_ID_to_name[[ID]]
      new_line <- c(sym_gene, name_path, ID, "1")
      reactome_adapt_df[nrow(reactome_adapt_df) + 1,] <- new_line
      
    }
  }
}

reactome_adapt_df$isAdaptiveReactome = 1
#```

### Bring together all databases with ReactomeDB

#```{r}
full_join_g = plyr::join_all(list(go_innate_df, go_adapt_df, go_other_df), type = "full")
full_join_k = plyr::join_all(list(kegg_innate_df, kegg_adapt_df), type = "full")
#full_join_r = plyr::join_all(list(reactome_innate_df, reactome_adapt_df), type = "full")
#full_join = plyr::join_all(list(full_join_g, full_join_k, 
#                                full_join_r, innatedb_df), type = "full")
full_join = plyr::join_all(list(full_join_g, full_join_k, innatedb_df), type = "full")

full_join$isInnateGO[is.na(full_join$isInnateGO)] = 0
full_join$isInnateKEGG[is.na(full_join$isInnateKEGG)] = 0
#full_join$isInnateReactome[is.na(full_join$isInnateReactome)] = 0
full_join$isInnateInnateDB[is.na(full_join$isInnateInnateDB)] = 0

full_join$isAdaptiveGO[is.na(full_join$isAdaptiveGO)] = 0
full_join$isAdaptiveKEGG[is.na(full_join$isAdaptiveKEGG)] = 0
#full_join$isAdaptiveReactome[is.na(full_join$isAdaptiveReactome)] = 0

full_join$isOtherGO[is.na(full_join$isOtherGO)] = 0

full_join$GO[is.na(full_join$GO)] = 0
full_join$InnateDB[is.na(full_join$InnateDB)] = 0
full_join$KEGG[is.na(full_join$KEGG)] = 0
#full_join$ReactomeDB[is.na(full_join$ReactomeDB)] = 0

full_join <- full_join %>% unique() 
#```

