---
title: "0.3_PathwayName_Examination"
author: "Ursula Widocki"
date: "6/28/2021"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
```

```{r}
library(tidyverse)
library(stringr)
library(stats)

library(ggpubr)
library(factoextra)
```

```{r}
immune_data = read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Data/immunity_genes_all.tsv", 
                         sep = "\t", stringsAsFactors = F, header = T, row.names = 1)

# Make all of the pathway names lowercase for similarity purposes
immune_data = immune_data %>%
  mutate(GOPathwayInnate = tolower(GOPathwayInnate)) %>%
  mutate(GOPathwayAdaptive = tolower(GOPathwayAdaptive)) %>%
  mutate(GOPathwayOther = tolower(GOPathwayOther)) %>%
  mutate(InnateDBPathway = tolower(InnateDBPathway)) %>%
  mutate(KEGGPathwayInnate = tolower(KEGGPathwayInnate)) %>%
  mutate(KEGGPathwayAdaptive = tolower(KEGGPathwayAdaptive)) %>%
  mutate(ReactomePathwayInnate = tolower(ReactomePathwayInnate)) %>%
  mutate(ReactomePathwayAdaptive = tolower(ReactomePathwayAdaptive)) %>%
  select(Symbol, GOPathwayAdaptive, GOPathwayInnate, GOPathwayOther, KEGGPathwayAdaptive, 
         KEGGPathwayInnate, ReactomePathwayInnate, ReactomePathwayAdaptive) %>%
  unique()

```



Look at each db path names and determine which need what kind of cleaning, if any

```{r}
# GO innate is fine
#look = (unique(immune_data$GOpathName.innate))
#look = look[!is.na(look)]
# GO adaptive is fine
#look = (unique(immune_data$GOpathName.adaptive))
#look = look[!is.na(look)]

# InnateDB names is most definitely not fine
#look = (unique(immune_data$InnateDBpathName))
#look = look[!is.na(look)]

# KEGG innate: Remove " - Homo sapiens (human)" from the end of each path
#look = (unique(immune_data$KEGGpathName.innate))
#look = look[!is.na(look)]
# KEGG adaptive: Remove " - Homo sapiens (human)" from the end of each string
#look = (unique(immune_data$KEGGpathName.adaptive))
#look = look[!is.na(look)]

# ReactomeDB innate: Remove "Homo sapiens: " from the beginning of each string
#look = (unique(immune_data$ReactomePathName.innate))
#look = look[!is.na(look)]
# ReactomeDB adaptive: Remove "Homo sapiens: " from the beginning of each string
#look = (unique(immune_data$ReactomePathName.adaptive))
#look = look[!is.na(look)]

```

# Make edits that are the same across all databases

```{r}
test_df = immune_data

# remove all terms between parentheses, replace "-" with " ", remove ","
test_df$GOPathwayInnate <- sub("\\s*\\([^\\)]+\\)", "", as.character(test_df$GOPathwayInnate))
test_df$GOPathwayInnate <- sub("-", " ", as.character(test_df$GOPathwayInnate)) # these two lines are not equal
test_df$GOPathwayInnate <- sub("-", " ", as.character(test_df$GOPathwayInnate)) # from keyboard
test_df$GOPathwayInnate <- sub(",", "", as.character(test_df$GOPathwayInnate))
test_df$GOPathwayAdaptive <- sub("\\s*\\([^\\)]+\\)","", as.character(test_df$GOPathwayAdaptive))
test_df$GOPathwayAdaptive <- sub("-", " ", as.character(test_df$GOPathwayAdaptive))
test_df$GOPathwayAdaptive <- sub("-", " ", as.character(test_df$GOPathwayAdaptive)) # from keyboard
test_df$GOPathwayAdaptive <- sub(",", "", as.character(test_df$GOPathwayAdaptive))

test_df$KEGGPathwayInnate <- sub("\\s*\\([^\\)]+\\)", "", as.character(test_df$KEGGPathwayInnate))
test_df$KEGGPathwayInnate <- sub("-", " ", as.character(test_df$KEGGPathwayInnate))
test_df$KEGGPathwayInnate <- sub("-", " ", as.character(test_df$KEGGPathwayInnate)) # from keyboard
test_df$KEGGPathwayInnate <- sub(",", "", as.character(test_df$KEGGPathwayInnate))
test_df$KEGGPathwayAdaptive <- sub("\\s*\\([^\\)]+\\)", "", as.character(test_df$KEGGPathwayAdaptive))
test_df$KEGGPathwayAdaptive <- sub("-", " ", as.character(test_df$KEGGPathwayAdaptive))
test_df$KEGGPathwayAdaptive <- sub("-", " ", as.character(test_df$KEGGPathwayAdaptive)) # from keyboard
test_df$KEGGPathwayAdaptive <- sub(",", "", as.character(test_df$KEGGPathwayAdaptive))

test_df$ReactomePathwayInnate <- sub("\\s*\\([^\\)]+\\)","", as.character(test_df$ReactomePathwayInnate))
test_df$ReactomePathwayInnate <- sub("-", " ", as.character(test_df$ReactomePathwayInnate))
test_df$ReactomePathwayInnate <- sub("-", " ", as.character(test_df$ReactomePathwayInnate)) # from keyboard
test_df$ReactomePathwayInnate <- sub(",", "", as.character(test_df$ReactomePathwayInnate))
test_df$ReactomePathwayAdaptive <- sub("\\s*\\([^\\)]+\\)","", as.character(test_df$ReactomePathwayAdaptive))
test_df$ReactomePathwayAdaptive <- sub("-", " ", as.character(test_df$ReactomePathwayAdaptive))
test_df$ReactomePathwayAdaptive <- sub("-", " ", as.character(test_df$ReactomePathwayAdaptive)) # from keyboard
test_df$RReactomePathwayAdaptive <- sub(",", "", as.character(test_df$ReactomePathwayAdaptive))
```

# Make edits that are database specific

Edit KEGG Path names
```{r}
test_df$KEGGPathwayInnate <- sub(pattern = "   homo sapiens", replacement = "", as.character(test_df$KEGGPathwayInnate), fixed = T)

test_df$KEGGPathwayAdaptive <- sub(pattern = "   homo sapiens", replacement = "", as.character(test_df$KEGGPathwayAdaptive), fixed = T)

```

Edit ReactomeDB Path names
```{r}
test_df$ReactomePathwayInnate <- sub(pattern = "homo sapiens: ", replacement =  "", as.character(test_df$ReactomePathwayInnate), fixed = T)

test_df$ReactomePathwayAdaptive <- sub(pattern = "homo sapiens: ", replacement =  "", as.character(test_df$ReactomePathwayAdaptive), fixed = T)

```


most_paths = c(test_df$GOpathName.innate, test_df$GOpathName.adaptive, test_df$KEGGpathName.innate, test_df$KEGGpathName.adaptive, test_df$ReactomePathName.adaptive, test_df$ReactomePathName.innate)
most_paths = most_paths[!is.na(most_paths)]
most_paths = unique(most_paths)
  
revigo_test <- paste(most_paths, collapse = '\n')

write.table(x = revigo_test, file = 'revigo_test.txt', row.names = F, col.names=F)



Edit InnateDB Path names
```{r}
sub_test_df = test_df %>%
  select(Symbol, InnateDBpathName) %>%
  mutate(Symbol = tolower(Symbol)) %>%
  mutate(InnateDBpathName = tolower(InnateDBpathName)) %>%
  unique() %>%
  na.omit()

# if gene from Symbol column is the first thing in path string, remove
for(i in seq(1:dim(sub_test_df)[1])){
  gene = sub_test_df$Symbol[i]
  path_name = sub_test_df$InnateDBpathName[i]
  path_sub = substr(path_name, start = 1, stop = nchar(gene))
  
  # test if gene is the in beginning of the path name
  if(path_sub == gene){
    path_sub = paste0(path_sub, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = " "
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = pattern # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  # next, if "is a" is first in the path string, remove
  pattern = "is a"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  # next, if "is " is first in the path string, remove
  pattern = "is"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  # next, if "plays a role in" is first is the path string, remove
  pattern = "plays a role in"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  # next, if "acts a" is first is the path string, remove
  pattern = "acts a"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "acts as a"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "an essential"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "an important"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "expression is"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "has a"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "has"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "involved in the"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "involved in"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "mediates"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "mediated"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "member of the"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "part of the"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "plays a central role in"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "plays a key role in"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "plays a key regulatory role in"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "plays an important role in"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "plays an essential role in"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "an"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "is a"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  pattern = "::"
  if(pattern == substr(path_name, start = 1, stop = nchar(pattern))){
    path_sub = paste0(pattern, " ") # add a space to remove space after gene name
    path_name = sub(pattern = path_sub, replacement = "", path_name)
  }
  
  sub_test_df$newPathName[i] = path_name
  
}
```

```{r}
# maybe figure out a way to remove all stop words from InnateDB?

```


```{r}
# try the clustering thing with the embeddings to see how things map out

require(magrittr)
require(word2vec)

GOPathwayNames = unique(c(test_df$GOPathwayInnate, test_df$GOPathwayAdaptive))
GOPathwayNames = GOPathwayNames[!is.na(GOPathwayNames)]

KEGGPathwayNames = unique(c(test_df$KEGGPathwayInnate, test_df$KEGGPathwayAdaptive))
KEGGPathwayNames = KEGGPathwayNames[!is.na(KEGGPathwayNames)]

ReactomePathwayNames = unique(c(test_df$ReactomePathwayInnate, test_df$ReactomePathwayAdaptive))
ReactomePathwayNames = ReactomePathwayNames[!is.na(ReactomePathwayNames)]

PathwayNames = unique(c(GOPathwayNames, KEGGPathwayNames, ReactomePathwayNames))

```


```{r}
model     <- read.word2vec("/Users/ursulawidocki/Desktop/BarabasiLab/Data/pubmed2018_w2v_400D/pubmed2018_w2v_400D.bin")
terms     <- summary(model, "vocabulary")
embedding <- as.matrix(model)

```

```{r}
pb <- txtProgressBar(min = 0, max = length(PathwayNames), style = 3)

# function that gets the average distance
average_dis = function(disease, e = embedding2){
  require(magrittr)
  
  t = rownames(e)
  dis = disease %>% 
    stringr::str_split(., " ", simplify = TRUE) %>% 
    as.character()
  
  t_in_dis = sum(t %in% dis)
  if(t_in_dis > 0){
    v =  e[t %in% dis,] %>% 
      matrix(., ncol = ncol(e)) %>% 
      colMeans(., na.rm = TRUE) %>% 
      as.data.frame()
    names(v)= disease
    return(v)
  }
}

lalala = PathwayNames %>% strsplit(., " ") %>% unlist() %>% unique()
embedding2 = embedding[rownames(embedding) %in% lalala, ]

average_dis(disease = PathwayNames[1000], e = embedding2)

require(parallel)
cl = parallel::makePSOCKcluster(10)
clusterExport(cl, "average_dis")
clusterExport(cl, "embedding2")

U = clusterApplyLB(cl, PathwayNames, average_dis)
U %<>% dplyr::bind_cols()

stopCluster(cl)

c = U %>% t %>% na.exclude() %>% philentropy::distance(., method = "cosine") # matrix with distance between diseases
xxx = U %>% t %>% na.exclude() %>% row.names()
colnames(c) = row.names(c) = xxx

```

```{r}
set.seed(123)
see =  U %>% t %>% na.exclude()

# to help choose the optimal number of kmeans clustering
fviz_nbclust(see, kmeans, method = "silhouette", k.max = 25) # 20
fviz_nbclust(see, kmeans, method = "wss", k.max = 50) # na
fviz_nbclust(see, kmeans, method = "gap_stat", k.max = 25) # 2
```

```{r}
km.res <- kmeans(x = see, centers = 2, nstart = 50, iter.max = 20)

fviz_cluster(km.res, data = see,
             geom = "point",
             ellipse.type = "convex", 
             labelsize = 8,
             ggtheme = theme_bw()
             )

fviz_cluster(km.res, data = see,
             geom = "text",
             ellipse.type = "convex", 
             labelsize = 8,
             ggtheme = theme_bw()
             )

km.res <- kmeans(x = see, centers = 20, nstart = 50, iter.max = 20)

fviz_cluster(km.res, data = see,
             geom = "point",
             ellipse.type = "convex", 
             labelsize = 12,
             ggtheme = theme_grey()
             )

fviz_cluster(km.res, data = see,
             geom = "text",
             ellipse.type = "convex", 
             labelsize = 12,
             ggtheme = theme_grey()
             )
```


```{r}
# Look at KEGG and Reactome

# matrix where rows are KEGG paths and cols are Reactome paths
K_ind = rownames(c)[which(rownames(c) %in% KEGGPathwayNames)]
R_ind = colnames(c)[which(colnames(c) %in% ReactomePathwayNames)]

KR_pathname_terms = c[K_ind, R_ind]

```

```{r}
# clustering 

```
















