---
title: "0.4_Immune_DB_ComplexUpset"
author: "Ursula Widocki"
date: "6/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ComplexUpset)
require(dplyr)
require(tidyr)
require(ggplot2)

library(ggplot2movies)
```

```{r}
immune_data = read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Data/immunity_genes_all.tsv", 
                         sep = "\t", stringsAsFactors = F, header = T, row.names = 1)
```


Tutorial
```{r}

movies = as.data.frame(ggplot2movies::movies)

genres = colnames(movies)[18:24]
movies[genres] = movies[genres] == 1

movies[movies$mpaa == '', 'mpaa'] = NA
movies = na.omit(movies)
```

```{r}
#set_size(8, 3)

upset(
    movies,
    genres,
    base_annotations=list(
        'Intersection size'=intersection_size(
            counts=TRUE,
            mapping=aes(fill=mpaa)
        )
    ),
    width_ratio=0.1
)
```


# Complex UpSet plot of databases
```{r}
immune_complex_plot <- immune_data %>% dplyr::select(Symbol, GO, KEGG, InnateDB, 
                                                     isInnateGO, isAdaptiveGO, isOtherGO, 
                                                     isInnateKEGG, isAdaptiveKEGG, isInnateInnateDB) %>%
  unique()

immune_complex_plot <- immune_complex_plot[!duplicated(immune_complex_plot), ]
#rownames(immune_complex_plot) <- immune_complex_plot$Symbol
databases = c("GO", "KEGG", "InnateDB")

#immune_complex_plot[databases] = immune_complex_plot[databases] == 1

#immune_complex_plot <- immune_complex_plot %>%
#  select(Symbol, GO, KEGG) 

# transform immune data
immune_complex_plot$ImmComp <- ifelse((immune_complex_plot$isInnateGO == 1 | immune_complex_plot$isInnateKEGG == 1 | immune_complex_plot$isInnateInnateDB == 1) & (immune_complex_plot$isAdaptiveGO == 0 & immune_complex_plot$isAdaptiveKEGG == 0) & (immune_complex_plot$isOtherGO == 0), "Innate", 
                                      ifelse((immune_complex_plot$isInnateGO == 0 & immune_complex_plot$isInnateKEGG == 0 & immune_complex_plot$isInnateInnateDB == 0) & (immune_complex_plot$isAdaptiveGO == 1 | immune_complex_plot$isAdaptiveKEGG == 1) & (immune_complex_plot$isOtherGO == 0), "Adaptive",
                                             ifelse((immune_complex_plot$isInnateGO == 0 & immune_complex_plot$isInnateKEGG == 0 & immune_complex_plot$isInnateInnateDB == 0) & (immune_complex_plot$isAdaptiveGO == 0 & immune_complex_plot$isAdaptiveKEGG == 0) & (immune_complex_plot$isOtherGO == 1), "General",
                                                    ifelse((immune_complex_plot$isInnateGO == 1 | immune_complex_plot$isInnateKEGG == 1 | immune_complex_plot$isInnateInnateDB == 1) & (immune_complex_plot$isAdaptiveGO == 1 | immune_complex_plot$isAdaptiveKEGG == 1) & (immune_complex_plot$isOtherGO == 0), "Innate&Adaptive", 
                                                           ifelse((immune_complex_plot$isInnateGO == 1 | immune_complex_plot$isInnateKEGG == 1 | immune_complex_plot$isInnateInnateDB == 1) & (immune_complex_plot$isAdaptiveGO == 0 & immune_complex_plot$isAdaptiveKEGG == 0) & (immune_complex_plot$isOtherGO == 1), "Innate&General",
                                                                  ifelse((immune_complex_plot$isInnateGO == 0 & immune_complex_plot$isInnateKEGG == 0 & immune_complex_plot$isInnateInnateDB == 0) & (immune_complex_plot$isAdaptiveGO == 1 | immune_complex_plot$isAdaptiveKEGG == 1) & (immune_complex_plot$isOtherGO == 1), "Adaptive&General",
                                                                         ifelse((immune_complex_plot$isInnateGO == 1 | immune_complex_plot$isInnateKEGG == 1 | immune_complex_plot$isInnateInnateDB == 1) & (immune_complex_plot$isAdaptiveGO == 1 | immune_complex_plot$isAdaptiveKEGG == 1) & (immune_complex_plot$isOtherGO == 1), "All_Components","None")))))))

```

```{r}
upset(
    immune_complex_plot,
    databases,
    base_annotations=list(
        'Intersection size'=intersection_size(
            counts=TRUE,
            mapping=aes(fill=ImmComp),
            bar_number_threshold = 1
        )+ scale_fill_manual(values=c(
            'Innate'='#00AFB5', 
            'Adaptive'='#FF0054',
            'Innate&Adaptive'='#9D4EDD', 
            'General'='#39CB5D',
            'Innate&General'='#0B4FE1',
            'Adaptive&General'='#FB5607',
            'All_Components'= 'grey44'
        ))
    ),
    width_ratio=0.1,
    wrap = T
) + ggtitle('Immune Databases and Immune Components')
```


# to add bars for databases
width_ratio=0.3,
    set_sizes=(
        upset_set_size(
            geom=geom_bar(
                aes(fill=ImmComp, x=group),
                width=0.8
            ) + scale_fill_manual(values=c(
            'Innate'='#00AFB5', 
            'Adaptive'='#FF0054',
            'Innate&Adaptive'='#9D4EDD', 
            'General'='#39CB5D',
            'Innate&General'='#0B4FE1',
            'Adaptive&General'='#FB5607',
            'All_Components'= 'black'
        )),
            position='left'
        )
    ),
    # moves legends over the set sizes
    guides='over'







upset(
    immune_complex_plot,
    databases,
    base_annotations=list(
        'Intersection size'=intersection_size(
            counts=FALSE,
            mapping=aes(fill=ImmComp)
        ) + scale_fill_manual(values=c(
            'Innate'='#00AFB5', 
            'Adaptive'='#FF0054',
            'Innate&Adaptive'='#9D4EDD', 
            'General'='#39CB5D',
            'Innate&General'='#0B4FE1',
            'Adaptive&General'='#FB5607',
            'All_Components'= 'black'
        ))
    ),
    width_ratio=0.1,
    set_sizes=(
        upset_set_size(
            geom=geom_bar(
                aes(fill=ImmComp, x=group),
                width=0.8
            ),
            position='right'
        )
    )
    # moves legends over the set sizes
    guides='over'
)

For Immune DB data
```{r}
debug <- immune_complex_plot %>%
  filter(GO == 0 & KEGG == 0 & InnateDB == 0)
```

```{r}
debug2 <- immune_complex_plot %>%
  filter(ImmComp == "None")
```



















