---
title: "2.0.3.1_Parallelize_Disease_Tissue_LCCs"
author: "Ursula Widocki"
date: "2/18/2022"
output: html_document
---

```{r}
rm(list=ls())
```

```{r}
library(tidyverse)
library(data.table)
`%ni%` <- Negate(`%in%`)
library(igraph)
library(superheat)
library(corrplot)
library(patchwork)
library(Cairo)
source("/Users/ursulawidocki/Desktop/BarabasiLab/NetMedTools.R")
```

```{r}
## Read in PPI data
ppi <- read.csv('/Users/ursulawidocki/Desktop/BarabasiLab/Vaccine/Data/PPI_Symbol_Entrez.csv')
ppi_df <- ppi[,c("Symbol_A", "Symbol_B")]

ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_B) & ppi_df$Symbol_B ==""), ]
ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_A) & ppi_df$Symbol_A ==""), ]

ppi_df$value = 1
ppi_df = ppi_df %>% unique()
ppi_g <- igraph::graph_from_data_frame(ppi_df, directed = F)
ppi_g <- simplify(ppi_g)

ppi_degree_df = data.frame(Degree = degree(graph = ppi_g)) %>%
  mutate(Gene = row.names(.))

## Read in gene-disease assoc data
GDA_data = read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Data/GDA_auto.csv", 
                      sep = ",", stringsAsFactors = F, header = T) # has isAutoimmune col
# select disease that have some form of Strong or Weak evidence and have more than 5 disease genes
GDA_auto = GDA_data %>%
  filter(Strong > 0 | 
           Weak > 0) %>%
  filter(hgnc_symbol %in% V(ppi_g)$name)%>% 
  group_by(NewName) %>%
  mutate(Total_Genes = n()) %>%
  filter(Total_Genes > 5) %>%
  filter(isAutoimmune == 1) %>%
  dplyr::select(NewName, hgnc_symbol) %>%
  unique()

## Read in tissue data


# read in autoimmune disease data to get dis with stat signif module
autoimmune_LCC_df = read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Data/AutoDis_LCCs.tsv", 
                               sep = "\t", stringsAsFactors = F, header = T)
rownames(autoimmune_LCC_df) <- autoimmune_LCC_df$Disease

autoimmune_LCC_df <- autoimmune_LCC_df %>% 
  mutate(padj = p.adjust(p_val, method = "fdr")) %>%
  mutate(signif = ifelse(padj < 0.05, "padj < 0.05", "padj > 0.05"))

signif_dis <- autoimmune_LCC_df %>%
  filter(padj < 0.05)
signif_dis <- signif_dis$Disease
```

tissues <- unique(tissues2.0_RNA$Tissue_Organ)
#tissue_LCC = list()
min_count = 10
reps = 1000
pb <- txtProgressBar(min = 0, max = ncol(tissue_matrix), style = 3)
final_LCCs = list()

for(i in 1:length(tissues)){
  setTxtProgressBar(pb, i)
  tiss =  tissues2.0_RNA %>% filter(Tissue_Organ == tissues[i])
  genes_in_tissue = tiss %>% filter(Unit > min_count)
  genes_in_tissue = unique(genes_in_tissue$Symbol)
  genes_in_tissue = genes_in_tissue[genes_in_tissue %in% V(ppi_g)$name]
  
  n_genes_tissue = length(genes_in_tissue)
  
  tissue_ppi = ppi_g %>% induced_subgraph(., genes_in_tissue)
  
  out = list()
  for(j in 1:length(signif_dis)){
    genes_disease = GDA_auto %>%
      filter(NewName %in% signif_dis[j]) %>%
      filter(hgnc_symbol %in% V(tissue_ppi)$name)
    n_genes_disease_tissue  = nrow(genes_disease)
    
    if(n_genes_disease_tissue > 0){
      LCC_disease_tissue = NetSci::LCC_Significance(N = reps, 
                                                    Targets = genes_disease$hgnc_symbol, 
                                                    G = tissue_ppi,
                                                    bins = 1
      )
      
      # store data
      tmp = data.frame(Disease_Name = signif_dis[j], 
                       Tissue = names(tissue_matrix)[i], 
                       Tissue_Genes = n_genes_tissue, 
                       Disease_Tissue_Genes = n_genes_disease_tissue, 
                       
                       LCC_size = LCC_disease_tissue$LCC, 
                       LCC_p = LCC_disease_tissue$emp_p)
      
      out[[j]] = tmp
    } else {
      
      tmp = data.frame(Disease_Name = signif_dis[j], 
                       Tissue = names(tissue_matrix)[i], 
                       Tissue_Genes = n_genes_tissue, 
                       Disease_Tissue_Genes = n_genes_disease_tissue, 
                       
                       LCC_size = 0, 
                       LCC_p = 1)
      
      out[[j]] = tmp
    }
  }  
  final_LCCs[[i]] = out %<>% bind_rows()
}

final_LCCs %<>% bind_rows()

```{r}
get_tissue_
```

