---
title: "2.4_Disease_Module_Sab_examination"
author: "Ursula Widocki"
date: "2022-08-12"
output: html_document
---

-> compute Sabs between autoimmune diseases in each tissue using GTEx DE genes
-> compare tissue Sab with Sab of diseases in PPI
-> evaluate disease module comorbidities in tissue
      if both diseases have a module in a tissue
      like a Jaccard similarity with tissue modules

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(data.table)
library(igraph)
library(ggraph)
library(NetSci)
library(magrittr)
library(stringr)
library(ggraph)
library(Cairo)

library(rdrop2)
drop_auth()

`%ni%` <- Negate(`%in%`)
```

```{r}
# Read in PPI
ppi <- fread('/Users/ursulawidocki/Desktop/BarabasiLab/Data/PPI_2022_04042022.csv')
ppi_df <- ppi[,c("HGNC_Symbol.1", "HGNC_Symbol.2")]

ppi_df = ppi_df[!(!is.na(ppi_df$HGNC_Symbol.2) & ppi_df$HGNC_Symbol.2 ==""), ]
ppi_df = ppi_df[!(!is.na(ppi_df$HGNC_Symbol.1) & ppi_df$HGNC_Symbol.1 ==""), ]

ppi_df$value = 1
ppi_df = ppi_df %>% unique()
ppi_g <- igraph::graph_from_data_frame(ppi_df, directed = F)
ppi_g <- simplify(ppi_g)

ppi_degree_df = data.frame(Degree = igraph::degree(ppi_g)) %>%
  mutate(Gene = row.names(.))

# autoimmune disease GDA data
GDA_data = fread("/Users/ursulawidocki/Desktop/BarabasiLab/Data/GDA_auto_new2.tsv") # has isAutoimmune col
# select disease that have some form of Strong or Weak evidence and have more than 5 disease genes
GDA_auto = GDA_data %>%
  filter(isAutoimmune == 1) %>%
  filter(Strong > 0 | 
           Weak > 0) %>%
  filter(HGNC_Symbol %in% V(ppi_g)$name) %>% 
  group_by(NewName) %>%
  mutate(Total_Genes = n()) %>%
  filter(Total_Genes > 5) %>%
  dplyr::select(NewName, HGNC_Symbol) %>%
  unique()

# Tissue data
# try this with just the hpa data
tissue_hpa_data = fread("/Users/ursulawidocki/Desktop/BarabasiLab/Data/rna_tissue_hpa.tsv")
tissue_dat <- tissue_hpa_data %>% dplyr::select(-Gene) %>% filter(`Gene name` %in% V(ppi_g)$name)
# if there is a duplicate, take the sum of their collective expression values
summary_hpa = tissue_dat %>% 
  group_by(Tissue, `Gene name`) %>%
  summarise(sum = sum(pTPM)) %>% 
  mutate(Q50 = quantile(sum, 0.50))

# Disease-Tissue LCCs
dis_tiss_LCC_df <- fread("/Users/ursulawidocki/Desktop/BarabasiLab/Data/Disease_Tissue_LCCs_HPA_newData2_Q50.tsv")
dis_tiss_LCC_df <- dis_tiss_LCC_df %>% filter(padj < 0.05)

# SAB from whole PPI
sab_whole_ppi <- fread("/Users/ursulawidocki/Desktop/BarabasiLab/Data/Autoimmune_jacc_sep2.tsv")
sab_whole_ppi %<>% dplyr::rename(Sab_ppi = Sab) %>% 
  dplyr::rename(p_Sab_ppi = p_Sab) %>% 
  dplyr::rename(padj_Sab_ppi = padj_Sab) %>% 
  dplyr::select(-Jacc) %>% 
  dplyr::select(-p_Jacc)

# Sab of diseases in tissues
sab_tissue <- fread("/Users/ursulawidocki/Desktop/BarabasiLab/Data/Disease_Tissue_Sab2.tsv")

```


# compute Sabs between autoimmune diseases in each tissue using HPA

```{r}
# reorder disease names 

n1 = apply(sab_tissue[, 1:2], 1, min)
n2 = apply(sab_tissue[, 1:2], 1, max)
sab_tissue$dis1 <- n1
sab_tissue$dis2 <- n2


n1 = apply(sab_whole_ppi[, 1:2], 1, min)
n2 = apply(sab_whole_ppi[, 1:2], 1, max)
sab_whole_ppi$dis1 <- n1
sab_whole_ppi$dis2 <- n2

# merge Sab data to plot distributions

all_sab <- left_join(sab_tissue, sab_whole_ppi)

```

```{r}
# to plot the Sab individually for all disease pairs
all_sab$dis_pair <- str_c(all_sab$dis1,"-", all_sab$dis2)
disease_pairs <- all_sab %>% pull(dis_pair) %>% unique()

for(pair in disease_pairs){
  print(pair)
  
  temp <- all_sab %>%
    filter(dis_pair == pair) 
  #filter for significant Sab_ppi
  
  plot <- ggplot(temp) +
    aes(x = Sab) +
    geom_histogram(bins = 30L, fill = "#112446") +
    geom_vline(xintercept = unique(temp$Sab_ppi), col = "red") +
    labs(title = pair, x = "Tissue Sab") +
    theme_minimal()
  
  print(plot)
  
}

```

# plot tissue Sab distributions with Sab from whole ppi
```{r}
# make distributions into a grid
p <- ggplot(all_sab) +
  aes(x = Sab) +
  geom_histogram(bins = 30L, fill = "#112446") +
  theme_minimal() +
  facet_grid(vars(dis1), vars(dis2))

p + geom_vline(aes(xintercept = Sab_ppi), data = all_sab, col = "red")
```








## Tissue Comorbidity Scores

# make a graph where the edge weight is the number of tissues the two diseases have significant Sab
```{r}
diseases <- unique(dis_tiss_LCC_df$Disease_Name)
col_labels <- c("Disease1", "Disease2", "NumTissuesDis1", "NumTissuesDis2", "TissueComorbidity")
dis_tis_comorb_df <- data.frame(matrix(ncol = length(col_labels), nrow = 0))
colnames(dis_tis_comorb_df) <- col_labels

k = 0
dis_tis_comorb_df = list()
for(i in 1:(length(diseases)-1)){
  # get tissues where disease has a module
  dis1 = diseases[i]
  dis1_df <- dis_tiss_LCC_df %>%
    filter(Disease_Name == dis1) %>%
    filter(padj < 0.05) %>%
    select(Disease_Name, Tissue)
  
  for(j in (i+1):(length(diseases))){
    # get tissues where disease has a module
    k=k+1
    dis2 = diseases[j]
    dis2_df <- dis_tiss_LCC_df %>%
      filter(Disease_Name == dis2) %>%
      filter(padj < 0.05) %>%
      select(Disease_Name, Tissue)
    
    # calc tissue comorbidity score
    tiss_dis1 <- unique(dis1_df$Tissue) # num tissues dis1
    tiss_dis2 <- unique(dis2_df$Tissue) # num tissues dis2
    
    inter <- intersect(tiss_dis1, tiss_dis2) # num tissues of both diseases
    total_tiss <- unique(union(tiss_dis1, tiss_dis2)) # total tissues between them

    com_score = length(inter) / length(total_tiss) # fraction of common and total tissues
    
    dis_tis_comorb_df[[k]] <- data.frame(Disease1 = dis1, Disease2 = dis2, NumTissueDis1 = length(tiss_dis1), NumTissueDis2 = length(tiss_dis2), TissueComorbidity = com_score) # save this as a df, not vect
    
    
  }
}
dis_tis_comorb_df %<>% bind_rows()
  
```

```{r}
df_for_graph <- dis_tis_comorb_df %>%
  select(Disease1, Disease2, TissueComorbidity)

tis_comb_g <- graph_from_data_frame(dis_tis_comorb_df, directed = F)
V(tis_comb_g)$degree <- degree(tis_comb_g)

#E(tis_comb_g)$TissueComorbidity <- as.numeric(E(tis_comb_g)$TissueComorbidity)

#ggraph(tis_comb_g , 'fr') +
#  geom_edge_hive(aes(#width = TissueComorbidity,
#                    alpha = TissueComorbidity)) +
#  geom_node_point(aes(size = degree)) +
#  geom_node_text(aes(label = name))+
#  theme_void()


# I want to plot it such that the higher the comorbidity score, the closer the nodes are together
set.seed(1255)
coord <- tis_comb_g %>%
  layout_with_drl(., weights = E(.)$TissueComorbidity * 7) %>%
  igraph::norm_coords()

plot(x = tis_comb_g,
     vertex.frame.color = NA,
     vertex.label.cex = V(tis_comb_g)$degree / 12,
     vertex.label.color = "black",
     vertex.label.degree = -pi/2, # how to move labels?
     vertex.label.dist = 0.1,
     vertex.label.family = "Helvetica",
     vertex.label.font = 2,
     vertex.size = 10,
     vertex.label.y = 3,
     
     edge.width = (E(tis_comb_g)$TissueComorbidity+0.1) * 2,
     edge.curved = 0.3,
     
     layout = coord
     )

```





# Some unexpected disease Sab tissue results

```{r}
# We want to examine Sabs where ppi < tissue

temp <- all_sab %>%
  filter(Sab_ppi < Sab) %>%
  filter(Sab_ppi < 0) %>%
  filter(Sab > 0)

```

# Examine UC and Glomerulonephritis
```{r}
# Plot disease modules on top of each other with each node being a pie chart of which disease they belong to

# plot the UC disease module in the ppi
uc_genes <- GDA_auto %>% filter(NewName == "colitis ulcerative") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)

g_uc <- induced_subgraph(ppi_g, uc_genes) #%>% extract_LCC()

# plot the glomerulonephritis disease module in the ppi
glom_genes <- GDA_auto %>% filter(NewName == "glomerulonephritis") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)

g_glom <- induced_subgraph(ppi_g, glom_genes) #%>% extract_LCC()

# plotting both disease modules
g_uc_glom <- induced_subgraph(ppi_g, c(glom_genes, uc_genes)) #%>% extract_LCC()

# add disease names as  feature
V(g_uc_glom)$UC <- ifelse(V(g_uc_glom)$name %in% uc_genes, 1, 0)
V(g_uc_glom)$Glom <- ifelse(V(g_uc_glom)$name %in% glom_genes, 1, 0)

vs = V(g_uc_glom)
values <- lapply(1:length(vs), function(x) c(V(g_uc_glom)$UC[x], V(g_uc_glom)$Glom[x]))

# use betweenness as an edge attribute
E(g_uc_glom)$weight <- edge_betweenness(g_uc_glom) %>% CoDiNA::normalize()


coord <- g_uc_glom %>%
  layout_with_fr(., weights = E(.)$weight *2.5) %>%
  igraph::norm_coords()

CairoPDF(paste0("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/UC_Glom_in_tissues/in_PPI.pdf"))
plot(g_uc_glom,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     edge.width = E(g_uc_glom)$weight,
     
     layout = coord)
title("UC and Glom in PPI")
dev.off()
```



# Graph tissue data
```{r}
uc_glom_tissues <- all_sab %>%
  filter(dis1 == "colitis ulcerative") %>%
  filter(dis2 == "glomerulonephritis") %>%
  pull(tissue)

# for loop over tissues
for(tiss in uc_glom_tissues){
  # get tissue genes
  genes_tiss <- tissue_data %>% filter(term == tiss) %>% pull(HGNC_Symbol)
  
  V(g_uc_glom)$UC_tiss <- V(g_uc_glom)$UC
  V(g_uc_glom)$Glom_tiss <- V(g_uc_glom)$Glom
  V(g_uc_glom)$tiss <- ifelse(V(g_uc_glom)$name %in% genes_tiss, 0, 1) # if in tiss, colorful pie
  for(gene in V(g_uc_glom)){
    if(V(g_uc_glom)$tiss[gene] == 1){
      V(g_uc_glom)$UC_tiss[gene] = 0
      V(g_uc_glom)$Glom_tiss[gene] = 0
    }
  }
  
  values <- lapply(1:length(vs), function(x) c(V(g_uc_glom)$UC_tiss[x], V(g_uc_glom)$Glom_tiss[x], V(g_uc_glom)$tiss[x]))
  
  # remove links between two genes that are not in the tissue
  genes_not_tissue <- V(g_uc_glom)$name[V(g_uc_glom)$name %ni% genes_tiss]
  g_uc_glom<- delete_edges(g_uc_glom, E(g_uc_glom) [.inc(genes_not_tissue)])

  # make sure to save figures in its own folder
  CairoPDF(paste0("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/UC_Glom_in_tissues/in_",tiss,".pdf"))
  plot(g_uc_glom,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF", "#D3D3D3")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     edge.width = E(g_uc_glom)$weight,
     
     layout = coord)
  title(paste0("UC and Glom in ", tiss))
  dev.off()
}
```


# RA and Glomerulonephritis
```{r}
# plot the RA disease module in the ppi
ra_genes <- GDA_auto %>% filter(NewName == "arthritis rheumatoid") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)
g_ra <- induced_subgraph(ppi_g, ra_genes) #%>% extract_LCC()

# plot the glomerulonephritis disease module in the ppi
glom_genes <- GDA_auto %>% filter(NewName == "glomerulonephritis") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)
g_glom <- induced_subgraph(ppi_g, glom_genes) #%>% extract_LCC()

# plotting both disease modules
g_ra_glom <- induced_subgraph(ppi_g, c(glom_genes, ra_genes)) #%>% extract_LCC()

# add disease names as  feature
V(g_ra_glom)$RA <- ifelse(V(g_ra_glom)$name %in% ra_genes, 1, 0)
V(g_ra_glom)$Glom <- ifelse(V(g_ra_glom)$name %in% glom_genes, 1, 0)

vs = V(g_ra_glom)
values <- lapply(1:length(vs), function(x) c(V(g_ra_glom)$RA[x], V(g_ra_glom)$Glom[x]))

# use betweenness as an edge attribute
E(g_ra_glom)$weight <- edge_betweenness(g_ra_glom) %>% CoDiNA::normalize()


coord <- g_ra_glom %>%
  layout_with_fr(., weights = E(.)$weight *2.5) %>%
  igraph::norm_coords()

CairoPDF(paste0("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/RA_Glom_in_tissues/in_PPI.pdf"))
plot(g_ra_glom,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     edge.width = E(g_ra_glom)$weight,
     
     layout = coord)
title("RA and Glom in PPI")
dev.off()
```

```{r}
ra_glom_tissues <- all_sab %>%
  filter(dis1 == "arthritis rheumatoid") %>%
  filter(dis2 == "glomerulonephritis") %>%
  pull(tissue)

# for loop over tissues
for(tiss in ra_glom_tissues){
  # get tissue genes
  genes_tiss <- tissue_data %>% filter(term == tiss) %>% pull(HGNC_Symbol)
  
  V(g_ra_glom)$RA_tiss <- V(g_ra_glom)$RA
  V(g_ra_glom)$Glom_tiss <- V(g_ra_glom)$Glom
  V(g_ra_glom)$tiss <- ifelse(V(g_ra_glom)$name %in% genes_tiss, 0, 1) # if in tiss, colorful pie
  for(gene in V(g_ra_glom)){
    if(V(g_ra_glom)$tiss[gene] == 1){
      V(g_ra_glom)$RA_tiss[gene] = 0
      V(g_ra_glom)$Glom_tiss[gene] = 0
    }
  }
  
  values <- lapply(1:length(vs), function(x) c(V(g_ra_glom)$RA_tiss[x], V(g_ra_glom)$Glom_tiss[x], V(g_ra_glom)$tiss[x]))
  
  genes_not_tissue <- V(g_ra_glom)$name[V(g_ra_glom)$name %ni% genes_tiss]
  g_ra_glom<- delete_edges(g_ra_glom, E(g_ra_glom) [.inc(genes_not_tissue)])

  # make sure to save figures in its own folder
  CairoPDF(paste0("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/RA_Glom_in_tissues/in_",tiss,".pdf"))
  plot(g_ra_glom,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF", "#D3D3D3")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     
     layout = coord)
  title(paste0("RA and Glom in ", tiss))
  dev.off()
}

```





# Anemia hemolytic and uveitis
```{r}
# plot the anemia disease module in the ppi
anemia_genes <- GDA_auto %>% filter(NewName == "anemia hemolytic") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)
g_anemia <- induced_subgraph(ppi_g, anemia_genes) #%>% extract_LCC()

# plot the uveitis disease module in the ppi
uve_genes <- GDA_auto %>% filter(NewName == "uveitis") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)
g_uve <- induced_subgraph(ppi_g, uve_genes) #%>% extract_LCC()

# plotting both disease modules
g_anemia_uve <- induced_subgraph(ppi_g, c(anemia_genes, uve_genes)) #%>% extract_LCC()

# add disease names as  feature
V(g_anemia_uve)$Anemia <- ifelse(V(g_anemia_uve)$name %in% anemia_genes, 1, 0)
V(g_anemia_uve)$Uve <- ifelse(V(g_anemia_uve)$name %in% uve_genes, 1, 0)

vs = V(g_anemia_uve)
values <- lapply(1:length(vs), function(x) c(V(g_anemia_uve)$Anemia[x], V(g_anemia_uve)$Uve[x]))

# use betweenness as an edge attribute
E(g_anemia_uve)$weight <- edge_betweenness(g_anemia_uve) %>% CoDiNA::normalize()


coord <- g_anemia_uve %>%
  layout_with_fr(., weights = E(.)$weight *2.5) %>%
  igraph::norm_coords()

CairoPDF(paste0("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/Anemia_Uveitis_in_tissues/in_PPI.pdf"))
plot(g_anemia_uve,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     
     layout = coord)
title("Anemia and Uveitis in PPI")
dev.off()
```

```{r}
anemia_uve_tissues <- all_sab %>%
  filter(dis1 == "anemia hemolytic") %>%
  filter(dis2 == "uveitis") %>%
  pull(tissue)

# for loop over tissues
for(tiss in anemia_uve_tissues){
  # get tissue genes
  genes_tiss <- tissue_data %>% filter(term == tiss) %>% pull(HGNC_Symbol)
  
  V(g_anemia_uve)$Anemia_tiss <- V(g_anemia_uve)$Anemia
  V(g_anemia_uve)$Uve_tiss <- V(g_anemia_uve)$Uve
  V(g_anemia_uve)$tiss <- ifelse(V(g_anemia_uve)$name %in% genes_tiss, 0, 1) # if in tiss, colorful pie
  for(gene in V(g_anemia_uve)){
    if(V(g_anemia_uve)$tiss[gene] == 1){
      V(g_anemia_uve)$Anemia_tiss[gene] = 0
      V(g_anemia_uve)$Uve_tiss[gene] = 0
    }
  }
  
  values <- lapply(1:length(vs), function(x) c(V(g_anemia_uve)$Anemia_tiss[x], V(g_anemia_uve)$Uve_tiss[x], V(g_anemia_uve)$tiss[x]))

  # make sure to save figures in its own folder
  CairoPDF(paste0("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/Anemia_Uveitis_in_tissues/in_",tiss,".pdf"))
  plot(g_anemia_uve,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF", "#D3D3D3")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     
     layout = coord)
  title(paste0("Anemia and Uveitis in ", tiss))
  dev.off()
}

```



# Juvenile arthritis and glomerulonephritis
```{r}
# plot the RA disease module in the ppi
ja_genes <- GDA_auto %>% filter(NewName == "arthritis juvenile") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)
g_ja <- induced_subgraph(ppi_g, ja_genes) #%>% extract_LCC()

# plot the glomerulonephritis disease module in the ppi
glom_genes <- GDA_auto %>% filter(NewName == "glomerulonephritis") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)
g_glom <- induced_subgraph(ppi_g, glom_genes) #%>% extract_LCC()

# plotting both disease modules
g_ja_glom <- induced_subgraph(ppi_g, c(glom_genes, ja_genes)) #%>% extract_LCC()

# add disease names as  feature
V(g_ja_glom)$JA <- ifelse(V(g_ja_glom)$name %in% ja_genes, 1, 0)
V(g_ja_glom)$Glom <- ifelse(V(g_ja_glom)$name %in% glom_genes, 1, 0)

vs = V(g_ja_glom)
values <- lapply(1:length(vs), function(x) c(V(g_ja_glom)$JA[x], V(g_ja_glom)$Glom[x]))

# use betweenness as an edge attribute
E(g_ja_glom)$weight <- edge_betweenness(g_ja_glom) %>% CoDiNA::normalize()


coord <- g_ja_glom %>%
  layout_with_fr(., weights = E(.)$weight *2.5) %>%
  igraph::norm_coords()

CairoPDF(paste0("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/JA_Glom_in_tissues/in_PPI.pdf"))
plot(g_ja_glom,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     
     layout = coord)
title("JA and Glom in PPI")
dev.off()
```

```{r}
ja_glom_tissues <- all_sab %>%
  filter(dis1 == "arthritis juvenile") %>%
  filter(dis2 == "glomerulonephritis") %>%
  pull(tissue)

# for loop over tissues
for(tiss in ja_glom_tissues){
  # get tissue genes
  genes_tiss <- tissue_data %>% filter(term == tiss) %>% pull(HGNC_Symbol)
  
  V(g_ja_glom)$JA_tiss <- V(g_ja_glom)$JA
  V(g_ja_glom)$Glom_tiss <- V(g_ja_glom)$Glom
  V(g_ja_glom)$tiss <- ifelse(V(g_ja_glom)$name %in% genes_tiss, 0, 1) # if in tiss, colorful pie
  for(gene in V(g_ja_glom)){
    if(V(g_ja_glom)$tiss[gene] == 1){
      V(g_ja_glom)$JA_tiss[gene] = 0
      V(g_ja_glom)$Glom_tiss[gene] = 0
    }
  }
  
  values <- lapply(1:length(vs), function(x) c(V(g_ja_glom)$JA_tiss[x], V(g_ja_glom)$Glom_tiss[x], V(g_ja_glom)$tiss[x]))

  # make sure to save figures in its own folder
  CairoPDF(paste0("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/JA_Glom_in_tissues/in_",tiss,".pdf"))
  plot(g_ja_glom,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF", "#D3D3D3")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     
     layout = coord)
  title(paste0("JA and Glom in ", tiss))
  dev.off()
}

```



# Alopecia areata and MS
```{r}
# plot the alopecia areata disease module in the ppi
alo_genes <- GDA_auto %>% filter(NewName == "alopecia areata") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)
g_alo <- induced_subgraph(ppi_g, alo_genes) #%>% extract_LCC()

# plot the MS disease module in the ppi
ms_genes <- GDA_auto %>% filter(NewName == "multiple sclerosis") %>% 
  filter(HGNC_Symbol %in% V(ppi_g)$name)%>% pull(HGNC_Symbol)
g_ms <- induced_subgraph(ppi_g, ms_genes) #%>% extract_LCC()

# plotting both disease modules
g_alo_ms <- induced_subgraph(ppi_g, c(alo_genes, ms_genes)) #%>% extract_LCC()

# add disease names as  feature
V(g_alo_ms)$Alopecia <- ifelse(V(g_alo_ms)$name %in% alo_genes, 1, 0)
V(g_alo_ms)$MS <- ifelse(V(g_alo_ms)$name %in% ms_genes, 1, 0)

vs = V(g_alo_ms)
values <- lapply(1:length(vs), function(x) c(V(g_alo_ms)$Alopecia[x], V(g_alo_ms)$MS[x]))

# use betweenness as an edge attribute
E(g_alo_ms)$weight <- edge_betweenness(g_alo_ms) %>% CoDiNA::normalize()


coord <- g_alo_ms %>%
  layout_with_fr(., weights = E(.)$weight *2.5) %>%
  igraph::norm_coords()

CairoPDF("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/Alopecia_MS_in_tissues/in_PPI.pdf")
plot(g_alo_ms,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     
     layout = coord)
title("Alopecia and MS in PPI")
dev.off()
```

```{r}
alo_ms_tissues <- all_sab %>%
  filter(dis1 == "alopecia areata") %>%
  filter(dis2 == "multiple sclerosis") %>%
  pull(tissue)

# for loop over tissues
for(tiss in alo_ms_tissues){
  # get tissue genes
  genes_tiss <- tissue_data %>% filter(term == tiss) %>% pull(HGNC_Symbol)
  
  V(g_alo_ms)$Alopecia_tiss <- V(g_alo_ms)$Alopecia
  V(g_alo_ms)$MS_tiss <- V(g_alo_ms)$MS
  V(g_alo_ms)$tiss <- ifelse(V(g_alo_ms)$name %in% genes_tiss, 0, 1) # if in tiss, colorful pie
  for(gene in V(g_alo_ms)){
    if(V(g_alo_ms)$tiss[gene] == 1){
      V(g_alo_ms)$Alopecia_tiss[gene] = 0
      V(g_alo_ms)$MS_tiss[gene] = 0
    }
  }
  
  values <- lapply(1:length(vs), function(x) c(V(g_alo_ms)$Alopecia_tiss[x], V(g_alo_ms)$MS_tiss[x], V(g_alo_ms)$tiss[x]))

  # make sure to save figures in its own folder
  CairoPDF(paste0("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/Figures/Alopecia_MS_in_tissues/in_",tiss,".pdf"))
  plot(g_alo_ms,
     vertex.shape = "pie",
     vertex.pie=values,
     vertex.pie.color = list(c("#8E3179", "#87C1FF", "#D3D3D3")),
     vertex.label = NA,
     vertex.size = 5,
     vertex.frame.color = NA,
     
     edge.curved = 0.1,
     
     layout = coord)
  title(paste0("Alopecia and MS in ", tiss))
  dev.off()
}

```
