---
title: "GDA_Auto_Innate"
author: "Ursula Widocki"
date: "5/2/2021"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())
```

```{r}
#library(dplyr)
library(MeSH.db)
library(MeSH.AOR.db)
library(VennDiagram)
library(gprofiler2)
source("/Users/ursulawidocki/Desktop/BarabasiLab//NetMedTools.R")
```


```{r}
GDA_data <- read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Vaccine/Data/GDA_18122020_ClassFromDisGeNet.csv", sep = ",", header = T, stringsAsFactors = F)

all_genes_df <- read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Vaccine/Data/all_genes.tsv", header = T, sep = "\t", stringsAsFactors = F)

ppi_df <- read.csv('/Users/ursulawidocki/Desktop/BarabasiLab/Vaccine/Data/PPI_Symbol_Entrez.csv')

ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_B) & ppi_df$Symbol_B ==""), ]
ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_A) & ppi_df$Symbol_A ==""), ]

ppi_df <- ppi_df[,c("Symbol_A", "Symbol_B")]
ppi_df$value = 1
ppi_df %>% unique()
ppi_g <- igraph::graph_from_data_frame(ppi_df, directed = F)
ppi_g %<>% simplify()

#ppi_degree_df = data.frame(Degree = degree(graph = ppi_g)) %>%
  #mutate(Gene = row.names(.))
```



### How are innate immunity genes associated with genes involved with autoimmune diseases

```{r}
cleaned_GDA = GDA_data %>%
  mutate(DiseaseName = tolower(DiseaseName)) %>%
  dplyr::select(hgnc_symbol, DiseaseName, DiseaseClass) %>%
  unique() 

# How many diseases are there # 1248

# How many genes are there # 12968

```

```{r}
## Filter by Immune System Disease

autoimmune_key <- "D001327"

# gets meshids of autoimmune diseases
auto_dis_ids <- MeSHDbi::select(MeSH.AOR.db, keys = autoimmune_key, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR")

auto_dis_ids_2 <- MeSHDbi::select(MeSH.AOR.db, keys = auto_dis_ids$OFFSPRING, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR")

auto_dis_ids_3 <- MeSHDbi::select(MeSH.AOR.db, keys = auto_dis_ids_2$OFFSPRING, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR")

auto_dis_ids_4 <- MeSHDbi::select(MeSH.AOR.db, keys = auto_dis_ids_3$OFFSPRING, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR")

#auto_dis_ids_5 <- select(MeSH.AOR.db, keys = auto_dis_ids_4$OFFSPRING, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR") # 0

all_terms <- rbind(auto_dis_ids,auto_dis_ids_2) %>% rbind(., auto_dis_ids_3) %>% rbind(., auto_dis_ids_4)
```

```{r}
# gets names of autoimmune diseases
parent_names <- MeSHDbi::select(MeSH.db, keys = all_terms$ANCESTOR, columns = c("MESHTERM"), keytype = "MESHID")
offspring_names <- MeSHDbi::select(MeSH.db, keys = all_terms$OFFSPRING, columns = c("MESHTERM"), keytype = "MESHID")

all_autodisease_names <- rbind(parent_names, offspring_names) %>% mutate(MESHTERM = tolower(MESHTERM)) %>% unique()

```

```{r}
# Use names and cleaned_GDA to get genes associated with autoimmune diseases

autoimmune_genes <- cleaned_GDA %>% dplyr::filter(cleaned_GDA$DiseaseName %in% all_autodisease_names$MESHTERM) # 690
autoimmune_genes$Type <- "Autoimmunity"
colnames(autoimmune_genes)[1] <- c("Symbol")

innateimmune_genes <- as.data.frame(all_genes_df$Symbol) %>% unique()
innateimmune_genes$Type <- "Innate Immunity"
colnames(innateimmune_genes)[1] <-c("Symbol")
```

# Make a plot looking at the number of diseases each gene is associated with
```{r}
auto_genes_disease_freq <- autoimmune_genes %>% 
  group_by(Symbol) %>% 
  summarise(DiseaseFreq = n())

auto_genes_disease_freq <- auto_genes_disease_freq %>% 
  group_by(DiseaseFreq) %>% 
  summarise(FreqCount = n())

ggplot(auto_genes_disease_freq) +
  aes(x = DiseaseFreq, y = FreqCount) +
  geom_point(shape = "circle", size = 4L, colour = "#112446") +
  labs(
    x = "Number of Diseases a Gene is Associated With",
    y = "Number of Genes with Said DIseases Association Frequency"
  ) +
  theme_minimal()

```




```{r}
# Make a venn diagram to look at the overlap
autos <- autoimmune_genes$Symbol
innates <- as.character(innateimmune_genes$Symbol)

venn.diagram(
  x = list(autos, innates),
  category.names = c("Autoimmunity" , "Innate Immunity"),
  filename = 'All_Innate_vs_Auto.png',
  height = 3000, 
  width = 4000,
  output=TRUE,
  main = "Autoimmunity Disease Assoc. Genes with All Innate Immunity"
)
```


# Overlap using Innate Immunity genes in PPI

```{r}
ppi_auto <- autos[autos %in% V(ppi_g)$name]

ppi_innate = innates[innates %in% V(ppi_g)$name]

venn.diagram(
  x = list(ppi_auto, ppi_innate),
  category.names = c("Autoimmunity" , "Innate Immunity"),
  filename = 'PPI_Innate_vs_Auto.png',
  height = 3000, 
  width = 4000,
  output=TRUE,
  main = "In PPI: Autoimmunity Disease Assoc. Genes with Innate Immunity"
)
```

# How does the overlap change if we consider only genes in 2 databases?

```{r}
all_pivot = all_genes_df %>% 
  dplyr::select(Symbol, GO, InnateDB, KEGG, ReactomeDB)%>% 
  tidyr::pivot_longer(., - Symbol) %>% 
  na.exclude()
```


```{r}
keep_2 = all_pivot %>% 
  group_by(Symbol) %>% 
  summarise(n = n()) %>%
  filter(n >= 2)

keep_2 = unique(keep_2$Symbol)
keep_2 <- keep_2[keep_2 %in% V(ppi_g)$name]

db2_graph <- induced_subgraph(ppi_g, keep_2)
temp <- components(db2_graph)$membership
db2_genes = unique(names(temp[temp == 1]))

venn.diagram(
  x = list(auto_in_ppi, db2_genes),
  category.names = c("Autoimmunity" , "Innate Immunity"),
  filename = 'PPI_LCC_Innate_2DB_vs_Auto.png',
  height = 3000, 
  width = 3000,
  output=TRUE,
  main = "Autoimmunity Disease Assoc. Genes vs LCC Innate Immunity (Genes in 2 Databases)"
)

```

# How does the overlap change if we consider only genes in 3 databases?

```{r}
keep_3 = all_pivot %>% 
  group_by(Symbol) %>% 
  summarise(n = n()) %>%
  filter(n >= 3)

keep_3 = unique(keep_3$Symbol)

keep_3 <- keep_3[keep_3 %in% V(ppi_g)$name]

db3_graph <- induced_subgraph(ppi_g, unique(keep_3))
temp <- components(db3_graph)$membership
db3_genes = unique(names(temp[temp == 1]))

venn.diagram(
  x = list(auto_in_ppi, db3_genes),
  category.names = c("Autoimmunity" , "Innate Immunity"),
  filename = 'PPI_LCC_Innate_3DB_vs_Auto.png',
  height = 3000, 
  width = 3000,
  output=TRUE,
  main = "Autoimmunity Disease Assoc. Genes vs LCC Innate Immunity (Genes in 3 Databases)"
)

```

# How does the overlap change if we consider only genes in 4 databases?

```{r}
# for intersect
keep_4 = all_pivot %>% 
  group_by(Symbol) %>% 
  summarise(n = n()) %>%
  filter(n == 4)

keep_4 = unique(keep_4$Symbol)

keep_4 <- keep_4[keep_4 %in% V(ppi_g)$name]

db4_graph <- induced_subgraph(ppi_g, unique(keep_4))
temp <- components(db4_graph)$membership
db4_genes = unique(names(temp[temp == 1]))

venn.diagram(
  x = list(auto_in_ppi, db4_genes),
  category.names = c("Autoimmunity" , "Innate Immunity"),
  filename = 'PPI_LCC_Innate_4DB_vs_Auto.png',
  height = 3000, 
  width = 3000,
  output=TRUE,
  main = "Autoimmunity Disease Assoc. Genes vs LCC Innate Immunity (Genes in 4 Databases)"
)
```


# Measure network separation

```{r}
## All genes in PPI

auto_df = autoimmune_genes[, c("Symbol","Type")]
#auto_df = auto_df[!duplicated(auto_df),] %>% na.omit()

innate_df <- innateimmune_genes[,c("Symbol","Type")]

all_df = rbind(auto_df, innate_df)

all_sep = module_sep(ppi_g, all_df)

sab_all = all_sep$Sab
sab_all[is.na(sab_all)] <- 0 # make NA 0
sab_all = sab_all + t(sab_all)

superheat(sab_all, pretty.order.rows = T, pretty.order.cols = T)


```


```{r}
## 2+ Databases
genes_in_2 <- as.data.frame(keep_2)
genes_in_2$Type <- "Innate 2+DB"
colnames(genes_in_2)[1] <- "Symbol"

sep2_df = rbind(auto_df, genes_in_2)

sep2 = module_sep(ppi_g, sep2_df)

sab_2 = sep2$Sab
sab_2[is.na(sab_2)] <- 0 # make NA 0
sab_2 = sab_2 + t(sab_2)

superheat(sab_2, pretty.order.rows = T, pretty.order.cols = T)
```

```{r}
## 3+ Database
genes_in_3 <- as.data.frame(keep_3)
genes_in_3$Type <- "Innate 3+DB"
colnames(genes_in_3)[1] <- "Symbol"

sep3_df = rbind(auto_df, genes_in_3)

sep3 = module_sep(ppi_g, sep3_df)

sab_3 = sep3$Sab
sab_3[is.na(sab_3)] <- 0 # make NA 0
sab_3 = sab_3 + t(sab_3)

superheat(sab_3, pretty.order.rows = T, pretty.order.cols = T)

```

```{r}
## 4 Databases

genes_in_4 <- as.data.frame(keep_4)
genes_in_4$Type <- "Innate 4+DB"
colnames(genes_in_4)[1] <- "Symbol"

sep4_df = rbind(auto_df, genes_in_4)

sep4 = module_sep(ppi_g, sep4_df)

sab_4 = sep4$Sab
sab_4[is.na(sab_4)] <- 0 # make NA 0
sab_4 = sab_4 + t(sab_4)

superheat(sab_4, pretty.order.rows = T, pretty.order.cols = T)

```

# What are the genes in the intersect? (Look at their symbol IDs)
```{r}
inter = intersect(all_genes_df$Symbol, autoimmune_genes$Symbol)

ind = str_order(
  inter,
  decreasing = FALSE,
  na_last = TRUE,
  locale = "en",
  numeric = FALSE,
)

inter[ind]

## CTLA, HLA, IFI, IFN, IL, MIR, PTPN, TNFRSF


```

# What autoimmune diseases are these genes associated with?
```{r}

intersect_diseases = cleaned_GDA[cleaned_GDA$hgnc_symbol %in% inter,]
which_diseases = unique(intersect_diseases$DiseaseName)
print(which_diseases) # 696 diseases / 1248 total diseases


```




## What functional pathways are these genes involved in?
```{r}
auto_innate_inter = autos[autos %in% innateimmune_genes$Symbol]
query_inter = unique(auto_innate_inter)

background_auto = unique(autoimmune_genes$Symbol)
background_innate = as.character(unique(innateimmune_genes$Symbol))
```


# Enrichment using Autoimmune genes as background
```{r}
enrich_bg_auto <- gost(query = query_inter, 
                organism = "hsapiens", ordered_query = FALSE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "fdr", 
                domain_scope = "custom", custom_bg = background_auto, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
```


# Enrichment using all innate immunity genes as background
```{r}
enrich_bg_innate <- gost(query = query_inter, 
                organism = "hsapiens", ordered_query = FALSE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "fdr", 
                domain_scope = "custom", custom_bg = background_innate, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)
```


```{r}
length(unique(enrich_bg_auto[["result"]][["term_name"]]))
length(unique(enrich_bg_innate[["result"]][["term_name"]]))

paths_auto = as.data.frame(unique(enrich_bg_auto[["result"]][["term_name"]]))
paths_innate = as.data.frame(unique(enrich_bg_innate[["result"]][["term_name"]]))

# look at the difference between the two analyses run
setdiff(unique(enrich_bg_auto[["result"]][["term_name"]]), unique(enrich_bg_innate[["result"]][["term_name"]]))

length(intersect(unique(enrich_bg_auto[["result"]][["term_name"]]), unique(enrich_bg_innate[["result"]][["term_name"]])))


## These two outcomes are all the same.

```

# There is something about the genes elimiated going form 3 -> 4 databases, so genes in 3 databases
```{r}
# How many genes are only in 3 databases

# Look at the symbol Ids og genes only in 3 data bases

# Enrichment of genes in 3 database

# Using only genes in 3 databases, what is the module separation?

```

