---
title: "0.1_Compile_Data"
author: "Ursula Widocki"
date: "6/7/2021"
output: html_document
---
#################################################################################################
# Makes the Immunity database
# 
#################################################################################################

```{r setup, include=FALSE}
rm(list = ls())
```

```{r}
library(tidyverse)
library(igraph)
library(dplyr)
require(magrittr)
```

```{r}
# Read in innate immunity data

go_i_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Data/godb_innate_genes.csv', 
                    header = T, sep = ",", row.names = 1, stringsAsFactors = F)
innate_i_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Data/innatedb_innate_genes.csv', 
                        header = T, sep = ",", row.names = 1, stringsAsFactors = F)
kegg_i_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Data/kegg_innate_genes.csv', 
                      header = T, sep = ",", row.names = 1, stringsAsFactors = F)
reactome_i_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Data/reactome_innate_genes.csv', 
                          header = T, sep = ",", row.names = 1, stringsAsFactors = F)

```

```{r}
# Read in adaptive immunity data

go_a_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Data/godb_adaptive_genes.csv', 
                    header = T, sep = ",", row.names = 1, stringsAsFactors = F)
kegg_a_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Data/kegg_adaptive_genes.csv', 
                      header = T, sep = ",", row.names = 1, stringsAsFactors = F)
reactome_a_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Data/reactome_adaptive_genes.csv', 
                          header = T, sep = ",", row.names = 1, stringsAsFactors = F)

```

```{r}
## Join all innate immunity dfs
full_i_join <- plyr::join_all(list(go_i_df, innate_i_df, kegg_i_df, reactome_i_df), type = "full")
full_i_join$isInnate = 1 # add a column to designate this is Innate Immunity 
colnames(full_i_join) <- c("Symbol" ,"GO", "GOID.innate", 
                           "GOpathName,innate", "InnateDBpathName", "InnateDB" , "KEGG", 
                           "KEGGpathID.innate", "KEGGpathName.innate", "ReactomePathName.innate",
                           "ReactomePathID.innate", "ReactomeDB", "isInnate")

## Join all adaptive immunity dfs
full_a_join <- plyr::join_all(list(go_a_df, kegg_a_df, reactome_a_df), type = "full")
full_a_join$isAdaptive = 1 # add a column to designate this is Adaptive Immunity 
colnames(full_a_join) <- c("Symbol" ,"GO" ,"GOID.adaptive" ,"GOpathName.adaptive" ,"KEGG" ,
                           "KEGGpathID.adaptive" ,"KEGGpathName.adaptive" ,"ReactomePathName.adaptive" ,
                           "ReactomePathID.adaptive" ,"ReactomeDB" ,"isAdaptive")


```

```{r}
## Combine all immunity datasets
full_join <- plyr::join_all(list(full_i_join, full_a_join), type = "full")

full_join$isInnate[is.na(full_join$isInnate)] = 0
full_join$isAdaptive[is.na(full_join$isAdaptive)] = 0

# In the database columns, make NA into 0
full_join$GO[is.na(full_join$GO)] = 0
full_join$KEGG[is.na(full_join$KEGG)] = 0
full_join$InnateDB[is.na(full_join$InnateDB)] = 0
full_join$ReactomeDB[is.na(full_join$ReactomeDB)] = 0

# makes sure only unique entries stay
full_join <- full_join %>% unique() # makes sure only unique entries stay

```

```{r}
write.table(full_join, "/Users/ursulawidocki/Desktop/BarabasiLab/Data/immunity_genes_all.tsv", sep = "\t", row.names = T, col.names = T)
```



```{r}
# which are in both innate and adaptive?

sub = full_join %>%
  filter(isAdaptive == 1) %>%
  filter(ReactomeDB == 1)

length(unique(sub$Symbol))

```









####################################################### Code I didn't use (Code that is here but shouldn't be)
```{r}
go <- gene_in_each[gene_in_each$GO == "GO.DB","Symbol"] %>% unique()
go <- go[!is.na(go)]
kegg <- gene_in_each[gene_in_each$KEGG == "KEGG.db","Symbol"] %>% unique()
kegg <- kegg[!is.na(kegg)]
innatedb <- gene_in_each[gene_in_each$InnateDB == "InnateDB","Symbol"] %>% unique()
innatedb <- innatedb[!is.na(innatedb)]
reactome <- gene_in_each[gene_in_each$ReactomeDB == "ReactomeDB","Symbol"] %>% unique()
reactome <- reactome[!is.na(reactome)]

fit <- euler(list(GO = go, KEGG = kegg, InnateDB = innatedb, ReactomeDB = reactome))

# Customize colors, remove borders, bump alpha, color labels white
plot(fit,
     fills = list(fill = c("red", "steelblue4", "turquoise3", "violet"), alpha = 0.4),
     labels = list(col = "white", font = 4),
     quantities = T, 
     shape = "ellipse")
```

```{r}
intersect_maybe = gene_in_each %>% drop_na()
```

```{r}
go <- gene_in_each[gene_in_each$GO == "GO.DB","Symbol"] %>% unique()
go <- go[!is.na(go)]
kegg <- gene_in_each[gene_in_each$KEGG == "KEGG.db","Symbol"] %>% unique()
kegg <- kegg[!is.na(kegg)]
innatedb <- gene_in_each[gene_in_each$InnateDB == "InnateDB","Symbol"] %>% unique()
innatedb <- innatedb[!is.na(innatedb)]

fit <- euler(list(GO = go, KEGG = kegg, InnateDB = innatedb))

# Customize colors, remove borders, bump alpha, color labels white
plot(fit,
     fills = list(fill = c("red", "steelblue4", "turquoise3"), alpha = 0.4),
     labels = list(col = "white", font = 4),
     quantities = T, 
     shape = "ellipse")
```

Without ReactomeDB, the intersect of the three relatively close databases is not all too different from the intersect with all four databases (126 vs 121, respectively).

```{r}

# Prepare a palette of 3 colors with R colorbrewer:
library(RColorBrewer)
myCol <- brewer.pal(4, "Pastel2")

venn.diagram(
        x = list(go, innatedb, kegg, reactome),
        category.names = c("GO" , "InnateDB" , "KEGG", "ReactomeBD"),
        filename = '#14_venn_diagramm.png',
        output=TRUE,
        
        # Circles
        lty = 'blank',
        fill = myCol,
        
        # Numbers
        cex = .7,
        fontface = "bold",
        fontfamily = "sans",
        
        # Set names
        cat.cex = 0.7,
        cat.fontface = "bold",
        cat.default.pos = "outer",
        cat.fontfamily = "sans"
)
```

# Jaccard Index of each database
```{r}
Similarity_normalized = function(GDA){
  g =  GDA %>% graph_from_data_frame(, directed = F)
  
  V(g)$type <- bipartite_mapping(g)$type
  # get the incidence matrix (or adjacency, depending on how the data was structured)
  A = as_incidence_matrix(g) %>% as.matrix()
  gg =   (A)  %*% Rfast::transpose(A)
  
  names(gg) = colnames(gg) = rownames(A)
  NORM = matrix(NA, ncol = ncol(gg), nrow = nrow(gg))
  # Normalize the values
  ADJ_for_DIS2DIS = gg
  pb <- txtProgressBar(min = 0, max = (ncol(NORM)), style = 3)
  for( i in 1:ncol(NORM)){
    setTxtProgressBar(pb, i)
    for(j in i:(nrow(NORM))){
      NORM[i,j] = NORM[j,i] = ADJ_for_DIS2DIS[i,j]/(ADJ_for_DIS2DIS[i,i]+ADJ_for_DIS2DIS[j,j]-ADJ_for_DIS2DIS[i,j])
    }
  }
  close(pb)
  
  Genes = diag(gg) %>% as.data.frame()
  Genes$ID = row.names(Genes)
  Genes$prop = (Genes$./ sum(Genes$.) )%>% CoDiNA::normalize()
  Genes$Count = Genes$.
  Genes = Genes[,-1]
  # Transform into a edge list
  rownames(NORM) = colnames(gg)
  colnames(NORM) = colnames(gg)
  G = NORM %>% wTO::wTO.in.line() 
  names(G)[3]="weight"
  
  return(G)
}

```

```{r}
## Jaccard of db

Data_db = go_df[,c("Symbol", "GO")] %>% unique()
colnames(Data_db)[2] = "Database"
temp = kegg_df[,c("Symbol", "KEGG")] %>% unique()
colnames(temp)[2] = "Database"
Data_db = rbind(Data_db, temp)
temp = innate_df[,c("Symbol", "InnateDB")] %>% unique()
colnames(temp)[2] = "Database"
Data_db = rbind(Data_db, temp)
temp = reactome_df[,c("Symbol", "ReactomeDB")] %>% unique()
colnames(temp)[2] = "Database"
Data_db = rbind(Data_db, temp)
Data_db = Data_db[c("Database", "Symbol")]


jacc_db <- Similarity_normalized(Data_db)
# make the Node columns string since it will treat EntrezIDs as ints
jacc_db$Node.1 <- as.character(jacc_db$Node.1)
jacc_db$Node.2 <- as.character(jacc_db$Node.2)
jacc_db$weight <- as.numeric(jacc_db$weight)

jacc_db_g <- graph.data.frame(jacc_db)
jacc_db_mat <- as.matrix(get.adjacency(jacc_db_g, attr='weight'))
jacc_db_mat <- jacc_db_mat + t(jacc_db_mat)
diag(jacc_db_mat) <- 1
#heatmap(jacc_path_mat, scale = "none")
superheat(jacc_db_mat, pretty.order.rows = T, pretty.order.cols=T, scale=F, heat.pal = c("white", "red"))

```

```{r}

bin_GO = which(genes_in_each)

# jaccard(<binary of GO>, <binary of y>)

```


# Do each db make an LCC?

```{r}
## GO LCC with all genes

#go_df <- subset(all_genes_df, all_genes_df$GO == "GO.DB")
# get GO genes that are the PPI
genes_go <- go_df[!duplicated(go_df$Symbol), "Symbol"] # has UBC
genes_go = genes_go[genes_go %in% V(ppi_g)$name]

LCC_go = LCC_signif(G = ppi_g, targets = genes_go, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_go$size, LCC_go$distribution)
hist(LCC_go$distribution, main = "GO LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_go$size, col = "red")

```

```{r}
## Distribution of degrees of genes removes from above (isolated nodes)

go_graph <- induced_subgraph(ppi_g, genes_go)
# get genes that are just in the LCC and remove genes that are isolated
temp <- components(go_graph)$membership
inLCC_go = names(temp[temp == 1])
nonLCC_go = names(temp[temp != 1])

nonLCC_go = names(temp[temp != 1])
not_go_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_go)

not_LCC_go_df <- not_go_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_go_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in LCC (GO)") +
  theme_minimal()

## Degree distribution of genes in the LCC

LCC_go_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_go) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_go_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in LCC (GO)") +
  theme_minimal()
```




## Looking Only at Innate DB

```{r}
## InnateDB with all genes

#innate_df <- subset(all_genes_df, all_genes_df$InnateDB == "InnateDB")
# get genes that are the PPI
genes_innate <- innate_df[!duplicated(innate_df$Symbol), "Symbol"]
genes_innate = genes_innate[genes_innate %in% V(ppi_g)$name]

LCC_innate = LCC_signif(G = ppi_g, targets = genes_innate, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_innate$size, LCC_innate$distribution)
hist(LCC_innate$distribution, main = "InnateDB LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_innate$size, col = "red")

```

```{r}
## Distribution of degrees of genes removes from above (isolated nodes)
innatedb_graph <- induced_subgraph(ppi_g, genes_innate)
temp <- components(innatedb_graph)$membership
nonLCC_innate = names(temp[temp != 1])
inLCC_innate = names(temp[temp == 1])

not_innate_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_innate)

not_LCC_innate_df <- not_innate_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_innate_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in LCC (InnateDB)") +
  theme_minimal()

# degree distribution of genes in the LCC

LCC_innate_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_innate) %>%
  group_by(Degree) %>%
  summarize(n = n())

# plot degrees of nodes in PPI
ggplot(LCC_innate_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Genes in LCC (InnateDB)") +
  theme_minimal()
```





## Looking Only at KEGG

```{r}
## KEGG LCC with all genes

#kegg_df <- subset(all_genes_df, all_genes_df$KEGG == "KEGG.db")
# get KEGG genes that are the PPI
genes_kegg <- kegg_df[!duplicated(kegg_df$Symbol), "Symbol"]
genes_kegg = genes_kegg[genes_kegg %in% V(ppi_g)$name]

LCC_kegg = LCC_signif(G = ppi_g, targets = genes_kegg, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_kegg$size, LCC_kegg$distribution)
hist(LCC_kegg$distribution, main = "KEGG LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_kegg$size, col = "red")
```

```{r}
## Distribution of degrees of genes removes from above (isolated nodes)
kegg_graph <- induced_subgraph(ppi_g, genes_kegg)
temp <- components(kegg_graph)$membership
nonLCC_kegg = names(temp[temp != 1])
inLCC_kegg = names(temp[temp == 1])

not_kegg_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_kegg)

not_LCC_df <- not_kegg_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in LCC (KEGG)") +
  theme_minimal()

## Degree distribution of genes in the LCC

LCC_kegg_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_kegg) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_kegg_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in LCC (KEGG)") +
  theme_minimal()
```



## Looking Only at Reactome

```{r}
## ReactomeDB LCC with all genes

#reactome_df <- subset(all_genes_df, all_genes_df$ReactomeDB == "ReactomeDB")
# Get ReactomeDB genes that are the PPI
genes_reactome <- reactome_df[!duplicated(reactome_df$Symbol), "Symbol"]
genes_reactome = genes_reactome[genes_reactome %in% V(ppi_g)$name]

LCC_reactome = LCC_signif(G = ppi_g, targets = genes_reactome, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

# Plotting
lim = c(LCC_reactome$size, LCC_reactome$distribution)
hist(LCC_reactome$distribution, main = "ReactomeDB LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_reactome$size, col = "red")
```

```{r}
## Distribution of degrees of genes removes from above (isolated nodes)
reactome_graph <- induced_subgraph(ppi_g, genes_reactome)
temp <- components(reactome_graph)$membership
nonLCC_reactome = names(temp[temp != 1])
inLCC_reactome = names(temp[temp == 1])

not_reactome_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_reactome)

not_LCC_df <- not_reactome_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in LCC (ReactomeDB)") +
  theme_minimal()

# degree distribution of genes in the LCC

LCC_reactome_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_reactome) %>%
  group_by(Degree) %>%
  summarize(n = n())

# plot degrees of nodes in PPI
ggplot(LCC_reactome_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in LCC (ReactomeDB)") +
  theme_minimal()
```




############# Now let's plot some of these distributions together

Now, let's plot the database distributions together
```{r}
plot_go <- hist(LCC_go$distribution)    
plot_innate <- hist(LCC_innate$distribution)   
plot_kegg <- hist(LCC_kegg$distribution)
plot_reactome <- hist(LCC_reactome$distribution)

plot( plot_go, col=rgb(0,1,0,1/2), border = F, xlim = c(450,1650), ylim = c(0, 300), main = "Histogram of Innate Immunity Database LCC Distributions")  # first histogram
plot( plot_innate, col=scales::alpha('red',.5), add=T, border = F)
plot( plot_kegg, col=scales::alpha('skyblue',.5),  add=T, border = F)
plot( plot_reactome, col=rgb(0,0,1,1/4),  add=T, border = F)
legend("top", c("GO", "InnateDB","KEGG", "ReactomeDB"), col=c(rgb(0,1,0,1/2), "red", "skyblue", rgb(0,0,1,1/4)), lwd=10)
```

# Separation of these LCCs

```{r}
# Bind the gene and labels together
go_temp = go_df[,c("Symbol", "GO")] %>% na.omit()
colnames(go_temp)[2] = "Label"
innatedb_temp = innate_df[,c("Symbol", "InnateDB")] %>% na.omit()
colnames(innatedb_temp)[2] = "Label"
kegg_temp = kegg_df[,c("Symbol", "KEGG")] %>% na.omit()
colnames(kegg_temp)[2] = "Label"
reactome_temp = reactome_df[,c("Symbol", "ReactomeDB")] %>% na.omit()
colnames(reactome_temp)[2] = "Label"


sep_labels = rbind(go_temp, innatedb_temp) %>% rbind(., kegg_temp) %>% rbind(., reactome_temp)

# Calc. Sep.
all_sep = module_sep(ppi_g, sep_labels)

sab_all = all_sep$Sab
sab_all[is.na(sab_all)] <- 0 # make NA 0
sab_all = sab_all + t(sab_all)

superheat(sab_all, pretty.order.rows = T, pretty.order.cols = T, bottom.label.text.angle = 90, heat.pal = c("blue", "white", "red"), left.label.text.size = 2, bottom.label.text.size = 3, heat.pal.values = c(0, 0.22, 1) )
```

# Look at separation as a network
```{r}

```



# Does innate immunity as a whole make a module?
```{r}
genes_all <- gene_in_each[!duplicated(gene_in_each$Symbol), "Symbol"]
genes_all = genes_all[genes_all %in% V(ppi_g)$name]

LCC_all_innate = LCC_signif(G = ppi_g, targets = genes_all, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

# Plotting
lim = c(LCC_all_innate$size, LCC_all_innate$distribution)
hist(LCC_all_innate$distribution, main = "All Innate Databases LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_all_innate$size, col = "red")
```

```{r}
## Distribution of degrees of genes removes from above (isolated nodes)
all_innate_graph <- induced_subgraph(ppi_g, genes_all)
temp <- components(all_innate_graph)$membership
nonLCC_all_innate = names(temp[temp != 1])
inLCC_all_innate = names(temp[temp == 1])

not_all_innate_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_all_innate)

not_LCC_df <- not_all_innate_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in LCC") +
  theme_minimal()

# degree distribution of genes in the LCC

LCC_all_innate_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_all_innate) %>%
  group_by(Degree) %>%
  summarize(n = n())

# plot degrees of nodes in PPI
ggplot(LCC_all_innate_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in LCC") +
  theme_minimal()
```








```{r}

sum(which(gene_in_each$Symbol %in% alias_dict$key)) # 2095999291
sum(which(gene_in_each$Symbol %in% alias_dict$GeneName)) # 4159453519
length(unique(gene_in_each$Symbol)) # 2811
length(unique(alias_dict$key)) # 413500

```


```{r}
# make gene_in_each long
temp = gene_in_each[,c("Symbol", "GO", "KEGG", "InnateDB", "ReactomeDB")] %>% unique() # add pathways later
all_genes_long = pivot_longer(temp, 
                              cols = c("GO", "KEGG", "InnateDB", "ReactomeDB"), 
                              )
all_genes_long$value2 = ifelse(is.na(all_genes_long$value), 0, 1)
all_genes_long$key = all_genes_long$Symbol

# merge alias_dict
temp = dplyr::left_join(all_genes_long, alias_dict)

# remove column with old gene names
temp_subset = temp[,c("GeneName", "value2", "name")] %>% unique() %>% na.omit()

new_map = temp_subset %>% pivot_wider(., names_from = name, 
                            values_from = value2, 
                            values_fn = length, 
                            values_fill = 0)
```

```{r}
go <- temp_subset[temp_subset$value == "GO.DB",c("key")] %>% unique()
go <- go[!is.na(go)]
kegg <- temp_subset[temp_subset$value == "KEGG.db",c("key")] %>% unique()
kegg <- kegg[!is.na(kegg)]
innatedb <- temp_subset[temp_subset$value == "InnateDB",c("key")] %>% unique()
innatedb <- innatedb[!is.na(innatedb)]
reactome <- temp_subset[temp_subset$value == "ReactomeDB",c("key")] %>% unique()
reactome <- reactome[!is.na(reactome)]

fit <- euler(list(GO = go, KEGG = kegg, InnateDB = innatedb, ReactomeDB = reactome))

# Customize colors, remove borders, bump alpha, color labels white
plot(fit,
     fills = list(fill = c("red", "steelblue4", "turquoise3", "violet"), alpha = 0.4),
     labels = list(col = "white", font = 4),
     quantities = T, 
     shape = "ellipse")
```

```{r}
go1 <- temp_subset[temp_subset$value == "GO.DB",c("GeneName")] %>% unique()
go1 <- go1[!is.na(go1)]
kegg1 <- temp_subset[temp_subset$value == "KEGG.db",c("GeneName")] %>% unique()
kegg1 <- kegg1[!is.na(kegg1)]
innatedb1 <- temp_subset[temp_subset$value == "InnateDB",c("GeneName")] %>% unique()
innatedb1 <- innatedb1[!is.na(innatedb1)]
reactome1 <- temp_subset[temp_subset$value == "ReactomeDB",c("GeneName")] %>% unique()
reactome1 <- reactome1[!is.na(reactome1)]

fit1 <- euler(list(GO = go1, KEGG = kegg1, InnateDB = innatedb1, ReactomeDB = reactome1))

# Customize colors, remove borders, bump alpha, color labels white
plot(fit1,
     fills = list(fill = c("red", "steelblue4", "turquoise3", "violet"), alpha = 0.4),
     labels = list(col = "white", font = 4),
     quantities = T, 
     shape = "ellipse")
```

```{r}

# maybe even look at which database benefits most from this alias conversion
```

```{r}
# do database separation and then make a network



```




