---
title: "InnateDB_immune_gene_curation"
author: "Ursula Widocki"
date: "12/10/2020"
output: html_document
---

```{r}
rm(list=ls())

library("tidyverse")
library("readxl")

```

## Try reading it straight from the website

url <- 'https://onlinecourses.science.psu.edu/stat501/sites/onlinecourses.science.psu.edu.stat501/files/data/leukemia_remission.txt'
df <- read.table(url, sep = '\t',header = TRUE, fileEncoding = "UTF-16LE")


## To download the entire database
# From https://www.innatedb.com/redirect.do?go=downloadCurated
file = "/Users/ursulawidocki/Desktop/BarabasiLab/Virome/Data/innatedb_all.mitab"

innate_df <- read.table(file, sep = '\t', header = TRUE)

## Keep human genes
sub <- "ENSG0"
human_gene_rows <- grepl(sub, innate_df$alt_identifier_A)

innate_df <- innate_df[human_gene_rows,]


## make a list with each gene only once

genes <- unique(innate_df$alt_identifier_A)
#genes <- unique(genes)
genes[[2]]



#######
## Innate Immunity genes

```{r}
## To download just the innate immunity genes

# From https://www.innatedb.com/annotatedGenes.do?type=innatedb
man_file <- "/Users/ursulawidocki/Desktop/BarabasiLab/Data/innatedb_curated_genes_innate_immunity.xls"

innate_genes_df <- read_xls(man_file)

innate_genes_df <- innate_genes_df[which(innate_genes_df$Species == "9606"),]

```

```{r}
## Add Database column

innate_genes_df$InnateDB <- rep("1",nrow(innate_genes_df))
innate_genes_df <- innate_genes_df[,c("Gene Symbol", "Annotation", "InnateDB")]
colnames(innate_genes_df) <- c("Symbol", "InnateDBpathName", "InnateDB")

```

```{r}
write.csv(innate_genes_df,'/Users/ursulawidocki/Desktop/BarabasiLab/Data/innatedb_innate_genes.csv')
```

Don't have EntrezID for IL29
MARCH5
TMEM173
Il25
Ticam2
DEFB4
Icosl
Smpdl3b
Ctnnb1
Gsk3a
Psen2
Stmn1
MB21D1
IL1F7
MIR203
Adrbk1
hsa-mir-146a
Il5
Kdm4a
Flt4
Nlrp1a
IL28B
Fscn1
C3ar1
Rheb
CTSL1
GNB2L1
Ifi202b
Numb
Marco
IL28A
Traf5
Mertk
Axl
PARK2
SFTPA1B;SFTPA1
hsa-mir-132
Mir497
MIR378
MS4A8B
Edil3
KIAA0226
TMED7;TICAM2
SELK
PLUNC
CD97
GPR77
Plg
CCBP2
MAP3K7IP1
TCEB2
AMACR;C1QTNF3
C19orf29
IL8
TCEB1
MoleculeID 32847
IL8RB
KDM1
MAP3K7IP2
hsa-mir-146b
Mknk1
hsa-mir-126
hsa-mir-98
hsa-let-7e
ERBB2IP
RP5-1000E10.4
MAP3K7IP3
APOBEC3G;APOBEC3F
hsa-mir-152
hsa-mir-148b
hsa-mir-148a
MIF;SLC2A11
TOMM70A
USP17
IFNAR2;IL10RB

############################################################## Code I didn't use



## Code to get the Entrez IDs for genes

library(org.Hs.eg.db)
hs <- org.Hs.eg.db
my.symbols <- c(innate_genes_df$`Gene Symbol`)
hs <- select(hs, 
       keys = my.symbols,
       columns = c("ENTREZID", "SYMBOL"),
       keytype = "SYMBOL")

hs$`Gene Symbol` <- hs$SYMBOL
hs <- hs[,2:3]

innate_genes_df <- cbind(innate_genes_df, hs)
innate_genes_df <- innate_genes_df[,1:6]

# Fix EntrezID column name
colnames(innate_genes_df) <- c("InnateDB.Gene.ID", "Gene.Symbol", "Species", "PubMED.ID","Annotation","EntrezID")


```{r}
innate_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Data/innatedb_innate_genes.csv', header = T, sep = ",", stringsAsFactors = F)
innate_df <- innate_df[,2:4]
```














































