---
title: "KEGG_immune_gene_curation"
author: "Ursula Widocki"
date: "12/10/2020"
output: html_document
---

```{r}
# KEGG.db: 
# KEGG R: 

rm(list=ls())

library("tidyverse")
#library("keggR")
library("KEGG.db") # Users who want more current data are encouraged to look at the KEGGREST or reactome.db packages

```
KEGG pathways I need:
"hsa04062" Chemokine signaling
"hsa04610" Complement and Coag
"hsa04611" Platelet Activ.
"hsa04612" antigen processing and presentation
"hsa04613" Neutrophil extracellular trap formation
"hsa04620" TLR signaling pathway
"hsa04621" NOD-like sig 
"hsa04622" RIG-I-like signaling
"hsa04623" Cytosolic DNA sensing
"hsa04625" C-type lectin signaling
"hsa04640" Hematopoietic cell lineage 
"hsa04650" NK cell pediated cytotoxicity 
"hsa04657" IL-17 signaling 
"hsa04664" Fc epsilon RI signal path
"hsa04670" Leuk. Trans. migration
"hsa04672" Intestinal IgA production



```{r}
#looking <- KEGGEXTID2PATHID
all_Kegg_paths <- KEGGPATHID2EXTID # human paths to Entrez genes

gene_to_path <- KEGGEXTID2PATHID

my_KEGG_paths <- c("hsa04062", "hsa04610","hsa04611", "hsa04612", "hsa04613","hsa04620", " hsa04621", "hsa04622", "hsa04623", "hsa04625", "hsa04640", "hsa04650", "hsa04657", "hsa04664", "hsa04670", "hsa04672")

```

```{r}
## Get KEGG information
col_labels <- c("EntrezID", "Symbol", "KEGGpathID", "Database")
kegg_df <- data.frame(matrix(ncol = length(col_labels), nrow = 0))
colnames(kegg_df) <- col_labels

# to add gene symbols
gene_human <- read_csv("/Users/ursulawidocki/Desktop/BarabasiLab/Data/gene_human.csv")
gene_human <- gene_human[,2:3]

#all_Kegg_paths[[my_KEGG_paths[1]]] # to look at Entrez genes

# for each innate immunity pathway
for (i in seq_len(length(my_KEGG_paths))){
  # get all genes in pathway i
  genes <- all_Kegg_paths[[my_KEGG_paths[i]]]
  
  for (g in genes){
    # get gene symbol
    if(g %in% gene_human$GeneID){
      sym_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
      
      # add all info to df
      temp <- c(g,sym_gene, my_KEGG_paths[i], "KEGG.db")
      kegg_df[nrow(kegg_df)+1,] <- temp  
      
    }
  }
}

```

```{r}

## Look at genes that were lost due to conversion


#length(unique(kegg_df$Symbol)) # should be 808

```

```{r}
## Save

write.csv(kegg_df,'/Users/ursulawidocki/Desktop/BarabasiLab/Data/kegg_innate_genes.csv')

```










## Code I didn't use

```{r}
kegg_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Data/kegg_innate_genes.csv', header = T, sep = ",")
kegg_df <- kegg_df[,2:4]
```


```{r}
# get total number of genes

genes_list <- c(kegg_df$EntrezID)

length(unique(genes_list)) # 799

```














