---
title: "0_Autoimmune_Diseases"
author: "Ursula Widocki"
date: "6/6/2021"
output: html_document
---

###############################################################################################
# This file uses the old GDA data, I think?
# Rewriting/ renaming of autoimmune diseases
#
# idk, this file is a mess
#
###############################################################################################

```{r setup, include=FALSE}
rm(list=ls())
```

```{r}
library(eulerr) # for venn diagrams, maybe try upSetR instead
library(gprofiler2) # gene enrichment
library(dplyr)
library(stringr)
library(stringdist)
library(superheat)
source("/Users/ursulawidocki/Desktop/BarabasiLab/NetMedTools.R")

set.seed(123) # for venn diagrams

```

```{r}
GDA_data <- read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Data/GDA_18122020_ClassFromDisGeNet.csv", sep = ",", header = T, stringsAsFactors = F)
GDA_data = GDA_data %>% filter(Strong > 0 | Weak > 0) %>% mutate(DiseaseName = tolower(DiseaseName)) %>% unique()

# Autoimmune Diseases
autoimmune_diseases <- read_tsv(file = "/Users/ursulawidocki/Desktop/BarabasiLab/Data/aarda_diseases_20210529.txt", 
                                col_names = F, col_types = cols()) %>% as.matrix() %>% t() %>% as.data.frame()
colnames(autoimmune_diseases)[1] <- "AutoDiseases"
autoimmune_diseases %<>% mutate(AutoDiseases = tolower(AutoDiseases))


# PPI
ppi_df <- read.csv('/Users/ursulawidocki/Desktop/BarabasiLab/Vaccine/Data/PPI_Symbol_Entrez.csv')

ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_B) & ppi_df$Symbol_B ==""), ]
ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_A) & ppi_df$Symbol_A ==""), ]

ppi_df <- ppi_df[,c("Symbol_A", "Symbol_B")]
ppi_df$value = 1
ppi_df = ppi_df %>% unique()
ppi_g <- igraph::graph_from_data_frame(ppi_df, directed = F)
ppi_g = ppi_g %<>% simplify()

ppi_degree_df = data.frame(Degree = degree(graph = ppi_g)) %>%
  mutate(Gene = row.names(.))
```

```{r}
# Get list of diseases in GDA data
# clean gene names

doesItWork_auto = gsub(pattern = "-", replacement = " ", x = autoimmune_diseases$AutoDiseases , ignore.case = T)
doesItWork_auto = gsub("[^0-9A-Za-z ]","" , doesItWork_auto,ignore.case = TRUE)
auto_disease_unique = unique(doesItWork_auto)

doesItWork_GDA = gsub(pattern = "-", replacement = " ", x = GDA_data$NewName, ignore.case = T)
doesItWork_GDA = gsub("[^0-9A-Za-z ]","" , doesItWork_GDA, ignore.case = TRUE)
GDA_disease_unique = unique(doesItWork_GDA)

name_dist = stringdistmatrix(a = auto_disease_unique, b = GDA_disease_unique, method = "cosine")
name_dist = name_dist %>% as.data.frame()
rownames(name_dist) = auto_disease_unique
colnames(name_dist) = GDA_disease_unique

```


```{r}
# look at the disease name distances using just cosine

potential_names_GDA = c()

for(i in seq(1:dim(name_dist)[1])){
  for(j in seq(1:dim(name_dist)[2])){
    if(name_dist[i,j] <= 0.01){
      #print(paste0("Row: ",  rownames(name_dist)[i], " Col: ",  colnames(name_dist)[j]))
      potential_names_GDA = c(potential_names_GDA, colnames(name_dist)[j])
    }
  }
}

length(unique(potential_names_GDA))
# cosine 0.01 : 47
# cosine 0.02 : 53 -> no false pos
# costine 0.03 : 56 -> 2 false pos

# also tried qgram at 0.01 : 34
# tanimoto 44
```

## Diseases that matched (GDA name): 
"addison disease",
"agammaglobulinemia",
"alopecia areata",
"amyloidosis",
"antiphospholipid syndrome",
"hepatitis autoimmune",
"pemphigoid bullous",
"castleman disease",
"celiac disease",
"chagas disease",
"dermatomyositis",
"endometriosis",
"eosinophilic esophagitis",
"giant cell arteritis",
"glomerulonephritis",
"granulomatosis with polyangiitis",
"graves disease",
"guillain barre syndrome",
"anemia hemolytic",
"purpura schoenlein henoch",
"hidradenitis suppurativa",
"myositis inclusion body",
"cystitis interstitial",
"arthritis juvenile",
"multiple sclerosis",
"myasthenia gravis",
"myositis",
"narcolepsy",
"neuromyelitis optica",
"neutropenia",
"optic neuritis",
"pemphigus",
"poems syndrome",
"polyarteritis nodosa",
"polymyositis",
"psoriasis",
"arthritis psoriatic",
"reflex sympathetic dystrophy",
"restless legs syndrome",
"arthritis rheumatoid",
"sarcoidosis",
"stiff person syndrome",
"takayasu arteritis",
"colitis ulcerative",
"uveitis",
"vasculitis",


## Other Mappings (from AARDA to GDA): 
"anti-gbm/anti-tbm nephritis" -> "anti glomerular basement membrane disease"
"behcets disease" -> "behcet syndrome",
"benign mucosal pemphigoid" -> "pemphigoid benign mucous membrane"
"type 1 diabetes" -> "diabetes mellitus type 1"
"autoimmune urticaria" -> "urticaria"
"lupus" -> "lupus erythematosus systemic"
"meniere’s disease" -> "meniere disease"
"mixed connective tissue disease"-> "connective tissue diseases"
"congenital heart block" -> "atrioventricular block"
"churg-strauss syndrome or eosinophilic granulomatosis" -> "churg strauss syndrome"
"crohn's disease" -> "crohn disease"
"fibrosing alveolitis" -> "idiopathic pulmonary fibrosis"
"parsonage turner syndrome" -> "brachial plexus neuritis"
"primary sclerosing cholangitis" -> "cholangitis sclerosing"
"raynauds phenomenon" -> "raynaud disease"
"hashimotos thyroiditis" -> "hashimoto disease"
"hashimotos thyroiditis" -> "thyroiditis autoimmune"
"herpes gestationis or pemphigoid gestationis" -> "pemphigoid gestationis"
"immune thrombocytopenic purpura" -> "purpura thrombocytopenic idiopathic"
"kawasaki disease" -> "mucocutaneous lymph node syndrome"
"lichen sclerosus" -> "vulvar lichen sclerosus"
"scleroderma" -> "scleroderma diffuse"
"scleroderma" -> "scleroderma systemic"
"scleroderma" -> "scleroderma limited"
"scleroderma" -> "scleroderma localized"
"sjögren’s syndrome" -> "sjogrens syndrome"
"susacs syndrome" -> "susac syndrome"
"thrombocytopenic purpura" -> "purpura thrombotic thrombocytopenic"
"thyroid eye disease" -> "graves ophthalmopathy"
"tolosa hunt syndrome" -> "ophthalmoplegia"
"tolosa hunt syndrome" -> "ophthalmoplegia chronic progressive external"
"undifferentiated connective tissue disease" -> "connective tissue diseases"

```{r}
final_auto_list <- c(read_tsv(file = "/Users/ursulawidocki/Desktop/BarabasiLab/Data/autoimmune_disease_naming_scheme.txt", 
                                col_names = F, col_types = cols())) %>% unlist()
```


# Make a file with all of the autoimmune diseases and genes
```{r}
# Change disease names to what I need them to be

#GDA_auto = GDA_data
GDA_data$OrigName = GDA_data$NewName

GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "thyroiditis autoimmune", 
                           replacement = "hashimoto disease", fixed = TRUE)

GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "scleroderma diffuse", 
                           replacement = "scleroderma", fixed = TRUE)
GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "scleroderma systemic", 
                           replacement = "scleroderma", fixed = TRUE)
GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "scleroderma limited", 
                           replacement = "scleroderma", fixed = TRUE)
GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "scleroderma localized", 
                           replacement = "scleroderma", fixed = TRUE)

GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "ophthalmoplegia chronic progressive external", 
                           replacement = "ophthalmoplegia", fixed = TRUE)

GDA_data$NewName = unlist(GDA_data$NewName)

```











####################  Old
# Read in data and set up their objects
```{r}
# Gene-disease association data
#GDA_data <- read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Data/Data_Clean_Complete.csv", sep = ",", header = T, stringsAsFactors = F)
#GDA_data = GDA_data %>% filter(Strong > 0 | Weak > 0) %>% mutate(NewName = tolower(NewName)) %>% unique()

GDA_data <- read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Data/GDA_18122020_ClassFromDisGeNet.csv", sep = ",", header = T, stringsAsFactors = F)
GDA_data = GDA_data %>% filter(Strong > 0 | Weak > 0) %>% mutate(DiseaseName = tolower(DiseaseName)) %>% unique()

# Autoimmune Diseases
autoimmune_diseases <- read_tsv(file = "/Users/ursulawidocki/Desktop/BarabasiLab/Data/aarda_diseases_20210529.txt", 
                                col_names = F, col_types = cols()) %>% as.matrix() %>% t() %>% as.data.frame()
colnames(autoimmune_diseases)[1] <- "AutoDiseases"
autoimmune_diseases %<>% mutate(AutoDiseases = tolower(AutoDiseases))


# PPI
ppi_df <- read.csv('/Users/ursulawidocki/Desktop/BarabasiLab/Vaccine/Data/PPI_Symbol_Entrez.csv')

ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_B) & ppi_df$Symbol_B ==""), ]
ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_A) & ppi_df$Symbol_A ==""), ]

ppi_df <- ppi_df[,c("Symbol_A", "Symbol_B")]
ppi_df$value = 1
ppi_df = ppi_df %>% unique()
ppi_g <- igraph::graph_from_data_frame(ppi_df, directed = F)
ppi_g = ppi_g %<>% simplify()

ppi_degree_df = data.frame(Degree = degree(graph = ppi_g)) %>%
  mutate(Gene = row.names(.))
```


# Get genes associated with these autoimmune diseases
```{r}
# Get list of diseases in GDA data
# clean gene names

doesItWork_auto = gsub(pattern = "-", replacement = " ", x = autoimmune_diseases$AutoDiseases , ignore.case = T)
doesItWork_auto = gsub("[^0-9A-Za-z ]","" , doesItWork_auto,ignore.case = TRUE)
auto_disease_unique = unique(doesItWork_auto)

doesItWork_GDA = gsub(pattern = "-", replacement = " ", x = GDA_data$NewName, ignore.case = T)
doesItWork_GDA = gsub("[^0-9A-Za-z ]","" , doesItWork_GDA, ignore.case = TRUE)
GDA_disease_unique = unique(doesItWork_GDA)

name_dist = stringdistmatrix(a = auto_disease_unique, b = GDA_disease_unique, method = "cosine")
name_dist = name_dist %>% as.data.frame()
rownames(name_dist) = auto_disease_unique
colnames(name_dist) = GDA_disease_unique

```

```{r}
# look at the disease name distances using just cosine

potential_names_GDA = c()

for(i in seq(1:dim(name_dist)[1])){
  for(j in seq(1:dim(name_dist)[2])){
    if(name_dist[i,j] <= 0.01){
      #print(paste0("Row: ",  rownames(name_dist)[i], " Col: ",  colnames(name_dist)[j]))
      potential_names_GDA = c(potential_names_GDA, colnames(name_dist)[j])
    }
  }
}

length(unique(potential_names_GDA))
# cosine 0.01 : 47
# cosine 0.02 : 53 -> no false pos
# costine 0.03 : 56 -> 2 false pos

# also tried qgram at 0.01 : 34
# tanimoto 44
```

## Diseases that matched (GDA name): 
"addison disease",
"agammaglobulinemia",
"alopecia areata",
"amyloidosis",
"antiphospholipid syndrome",
"hepatitis autoimmune",
"pemphigoid bullous",
"castleman disease",
"celiac disease",
"chagas disease",
"dermatomyositis",
"endometriosis",
"eosinophilic esophagitis",
"giant cell arteritis",
"glomerulonephritis",
"granulomatosis with polyangiitis",
"graves disease",
"guillain barre syndrome",
"anemia hemolytic",
"purpura schoenlein henoch",
"hidradenitis suppurativa",
"myositis inclusion body",
"cystitis interstitial",
"arthritis juvenile",
"multiple sclerosis",
"myasthenia gravis",
"myositis",
"narcolepsy",
"neuromyelitis optica",
"neutropenia",
"optic neuritis",
"pemphigus",
"poems syndrome",
"polyarteritis nodosa",
"polymyositis",
"psoriasis",
"arthritis psoriatic",
"reflex sympathetic dystrophy",
"restless legs syndrome",
"arthritis rheumatoid",
"sarcoidosis",
"stiff person syndrome",
"takayasu arteritis",
"colitis ulcerative",
"uveitis",
"vasculitis",


## Other Mappings (from AARDA to GDA): 
"anti-gbm/anti-tbm nephritis" -> "anti glomerular basement membrane disease"
"behcets disease" -> "behcet syndrome",
"benign mucosal pemphigoid" -> "pemphigoid benign mucous membrane"
"type 1 diabetes" -> "diabetes mellitus type 1"
"autoimmune urticaria" -> "urticaria"
"lupus" -> "lupus erythematosus systemic"
"meniere’s disease" -> "meniere disease"
"mixed connective tissue disease"-> "connective tissue diseases"
"congenital heart block" -> "atrioventricular block"
"churg-strauss syndrome or eosinophilic granulomatosis" -> "churg strauss syndrome"
"crohn's disease" -> "crohn disease"
"fibrosing alveolitis" -> "idiopathic pulmonary fibrosis"
"parsonage turner syndrome" -> "brachial plexus neuritis"
"primary sclerosing cholangitis" -> "cholangitis sclerosing"
"raynauds phenomenon" -> "raynaud disease"
"hashimotos thyroiditis" -> "hashimoto disease"
"hashimotos thyroiditis" -> "thyroiditis autoimmune"
"herpes gestationis or pemphigoid gestationis" -> "pemphigoid gestationis"
"immune thrombocytopenic purpura" -> "purpura thrombocytopenic idiopathic"
"kawasaki disease" -> "mucocutaneous lymph node syndrome"
"lichen sclerosus" -> "vulvar lichen sclerosus"
"scleroderma" -> "scleroderma diffuse"
"scleroderma" -> "scleroderma systemic"
"scleroderma" -> "scleroderma limited"
"scleroderma" -> "scleroderma localized"
"sjögren’s syndrome" -> "sjogrens syndrome"
"susacs syndrome" -> "susac syndrome"
"thrombocytopenic purpura" -> "purpura thrombotic thrombocytopenic"
"thyroid eye disease" -> "graves ophthalmopathy"
"tolosa hunt syndrome" -> "ophthalmoplegia"
"tolosa hunt syndrome" -> "ophthalmoplegia chronic progressive external"
"undifferentiated connective tissue disease" -> "connective tissue diseases"

```{r}
final_auto_list <- c(read_tsv(file = "/Users/ursulawidocki/Desktop/BarabasiLab/Data/autoimmune_disease_naming_scheme.txt", 
                                col_names = F, col_types = cols())) %>% unlist()
```


# Make a file with all of the autoimmune diseases and genes
```{r}
# Change disease names to what I need them to be

#GDA_auto = GDA_data
GDA_data$OrigName = GDA_data$NewName

GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "thyroiditis autoimmune", 
                           replacement = "hashimoto disease", fixed = TRUE)

GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "scleroderma diffuse", 
                           replacement = "scleroderma", fixed = TRUE)
GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "scleroderma systemic", 
                           replacement = "scleroderma", fixed = TRUE)
GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "scleroderma limited", 
                           replacement = "scleroderma", fixed = TRUE)
GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "scleroderma localized", 
                           replacement = "scleroderma", fixed = TRUE)

GDA_data$NewName <- lapply(GDA_data$NewName, gsub, pattern = "ophthalmoplegia chronic progressive external", 
                           replacement = "ophthalmoplegia", fixed = TRUE)

GDA_data$NewName = unlist(GDA_data$NewName)

```

```{r}
GDA_auto = GDA_data[GDA_data$NewName %in% final_auto_list,] %>% unique()

write.table(GDA_data, file = "/Users/ursulawidocki/Desktop/BarabasiLab/Data/GDA_data.csv", sep = ",", row.names = F, col.names = T)
write.table(GDA_auto, file = "/Users/ursulawidocki/Desktop/BarabasiLab/Data/GDA_auto.csv", sep = ",", row.names = F, col.names = T)

```




















