---
title: "ReactomeDB_immune_gene_curation"
author: "Ursula Widocki"
date: "12/9/2020"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

```


```{r}

# Manual: http://bioconductor.org/packages/release/data/annotation/manuals/reactome.db/man/reactome.db.pdf
# How to: https://bioc.ism.ac.jp/packages/2.8/data/annotation/vignettes/reactome.db/inst/doc/reactome.pdf


library(reactome.db)
library(tidyverse)

```

## List of ReactomeDB pathways I know I need 
# as written on the website interface

#### "Toll-like Receptor Cascades"
"Homo sapiens: Toll-like Receptor Cascades"

#### "Complement cascade"
"Homo sapiens: Complement cascade"

#### "Nucleotide-binding domain, leucine rich repeat containing recptor (NLR) signaling pathways"
"Homo sapiens: Nucleotide-binding domain, leucine rich repeat containing receptor (NLR) signaling pathways"

#### "Advanced glycosylation endproduct receptor signaling"
"Homo sapiens: Advanced glycosylation endproduct receptor signaling"

#### "DDX58/IFIH1-mediated induction of interferon-alpha/beta"
"Homo sapiens: DDX58/IFIH1-mediated induction of interferon-alpha/beta"

#### "Cytosolic sensors of pathogen-associated DNA"
"Homo sapiens: Cytosolic sensors of pathogen-associated DNA "

#### "Fcgamma receptor (FCGR) dependent phagocytosis"
"Homo sapiens: Fcgamma receptor (FCGR) dependent phagocytosis"

#### "DAP12 interactions"
"Homo sapiens: DAP12 interactions"

#### "Fc epsilon receptor (FCERI) signaling"
"Homo sapiens: Fc epsilon receptor (FCERI) signaling"

#### "C-type lectin receptors (CLRs)"
"Homo sapiens: C-type lectin receptors (CLRs)"

#### "Antimicrobial peptides"
"Homo sapiens: Antimicrobial peptides"

#### "Neutrophil degranulation"
"Homo sapiens: Neutrophil degranulation"

#### "ROS and RNS production in phagocytes"
"Homo sapiens: ROS and RNS production in phagocytes"

#### "Alpha-protein kinase 1 signaling pathway"
"Homo sapiens: Alpha-protein kinase 1 signaling pathway"

#### "Interferon Signaling"
"Homo sapiens: Interferon Signaling"

#### "Signaling by Interleukins"
"Homo sapiens: Signaling by Interleukins"

#### "Prolactin receptor signaling"
"Homo sapiens: Prolactin receptor signaling"

#### "TNFR2 non-canonical FN-kB pathway"
"Homo sapiens: TNFR2 non-canonical NF-kB pathway"

#### "FLT3 Signaling"
"Homo sapiens: FLT3 Signaling"

"Homo sapiens: Signaling by CSF3 (G-CSF)"

```{r}
## List of all pathways I need

paths <- c("Homo sapiens: Toll-like Receptor Cascades", 
           "Homo sapiens: Complement cascade", 
           "Homo sapiens: Nucleotide-binding domain, leucine rich repeat containing receptor (NLR) signaling pathways", 
           "Homo sapiens: Advanced glycosylation endproduct receptor signaling", 
           "Homo sapiens: DDX58/IFIH1-mediated induction of interferon-alpha/beta", 
           "Homo sapiens: Cytosolic sensors of pathogen-associated DNA ", 
           "Homo sapiens: Fcgamma receptor (FCGR) dependent phagocytosis", 
           "Homo sapiens: DAP12 interactions", 
           "Homo sapiens: Fc epsilon receptor (FCERI) signaling", 
           "Homo sapiens: C-type lectin receptors (CLRs)", 
           "Homo sapiens: Antimicrobial peptides", 
           "Homo sapiens: Neutrophil degranulation", 
           "Homo sapiens: ROS and RNS production in phagocytes", 
           "Homo sapiens: Alpha-protein kinase 1 signaling pathway", 
           "Homo sapiens: Interferon Signaling", 
           "Homo sapiens: Signaling by Interleukins", 
           "Homo sapiens: Prolactin receptor signaling", 
           "Homo sapiens: TNFR2 non-canonical NF-kB pathway", 
           "Homo sapiens: FLT3 Signaling",
           "Homo sapiens: Signaling by CSF3 (G-CSF)")

```

```{r}
## Read in information in ReactomeDB that we need

reactomeIDs <- reactomePATHNAME2ID # maps Reactome path identifiers to reactomeIDs
entrezGenes <- reactomePATHID2EXTID # maps reactome IDs to Entrez gene names
entrez_to_ID <- reactomeEXTID2PATHID
path_ID_to_name <- reactomePATHID2NAME

#xx <- as.list(reactomeGO2REACTOMEID)
#all_reactomeIds <- ls(reactomePATHID2EXTID)

#test <- ls(reactomePATHNAME2ID) # when printed, shows all of the pathway names in database
#test[10004:11000] # Homo sapiens starts at 10004

```

Using the pathway names, we first get the reactome IDs and then path IDs to get the Entrez gene IDs of the genes involved in the innate immune system and cytokine signaling pathways above.

```{r}
# Get all Reactome IDs for all of the paths
path_IDs <- c()
for (path in paths){
  path_IDs <- append(path_IDs, reactomeIDs[[path]])
  
}

# set up df to store genes and paths
col_labels <- c("Symbol", "ReactomePathName", "ReactomePathID", "ReactomeDB")
reactome_df <- data.frame(matrix(ncol = length(col_labels), nrow = 0))
colnames(reactome_df) <- col_labels

# to add gene symbols
gene_human <- read_csv("/Users/ursulawidocki/Desktop/BarabasiLab/Data/gene_human.csv")
gene_human <- gene_human[,2:3]

for (ID in path_IDs){
  reactome_genes = entrezGenes[[ID]] # gets all Entrez genes in paths
  
  for(g in reactome_genes){
    if(g %in% gene_human$GeneID){
      sym_gene <- gene_human[which(gene_human$GeneID == g),"Symbol"]
      name_path <- path_ID_to_name[[ID]]
      new_line <- c(sym_gene, name_path, ID, "1")
      reactome_df[nrow(reactome_df) + 1,] <- new_line
      
    }
  }
}

```

```{r}
## Saves the df to integrate information later

write.csv(reactome_df,'/Users/ursulawidocki/Desktop/BarabasiLab/Data/reactome_innate_genes.csv', col.names = TRUE)

```










############################################################## Code I didn't use

```{r}
reactome_df <- read.table('/Users/ursulawidocki/Desktop/BarabasiLab/Virome/Data/reactome_genes.csv', header = T, sep = ",")
reactome_df <- reactome_df[,2:5]
```


```{r}
# get total number of genes

genes_list <- c(reactome_df$EntrezID)

length(unique(genes_list)) # 1668 unique genes

```
















