---
title: "1_Innate_Autoimmune_Overlap"
author: "Ursula Widocki"
date: "5/11/2021"
output: html_document
---
#################################################################################################
# Original autoimmune disease module-looking-at-things file
# 
#
# 
#################################################################################################
```{r setup, include=FALSE}
rm(list=ls())
```

```{r}
library(MeSH.db)
library(MeSH.AOR.db)
library(eulerr)
library(gprofiler2) # gene enrichment
#library(stringdist)
library(dplyr)
library(stringr)
source("/Users/ursulawidocki/Desktop/BarabasiLab/NetMedTools.R")

set.seed(123) # for venn diagrams

```

# Read in data and set up their objects
```{r}
GDA_data <- read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Vaccine/Data/GDA_18122020_ClassFromDisGeNet.csv", sep = ",", header = T, stringsAsFactors = F)

GDA_data = GDA_data %>% filter(Strong > 0 | Weak > 0) %>% mutate(DiseaseName = tolower(DiseaseName)) %>% unique()

all_genes_df <- read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Vaccine/Data/all_genes.tsv", header = T, sep = "\t", stringsAsFactors = F)

ppi_df <- read.csv('/Users/ursulawidocki/Desktop/BarabasiLab/Vaccine/Data/PPI_Symbol_Entrez.csv')

ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_B) & ppi_df$Symbol_B ==""), ]
ppi_df = ppi_df[!(!is.na(ppi_df$Symbol_A) & ppi_df$Symbol_A ==""), ]

ppi_df <- ppi_df[,c("Symbol_A", "Symbol_B")]
ppi_df$value = 1
ppi_df = ppi_df %>% unique()
ppi_g <- igraph::graph_from_data_frame(ppi_df, directed = F)
ppi_g = ppi_g %<>% simplify()

ppi_degree_df = data.frame(Degree = degree(graph = ppi_g)) %>%
  mutate(Gene = row.names(.))
```

### How are innate immunity genes associated with genes involved with autoimmune diseases

# Get MeSH terms
```{r}
## Filter by Immune System Disease

autoimmune_key <- "D001327"

# gets meshids of autoimmune diseases
auto_dis_ids <- MeSHDbi::select(MeSH.AOR.db, keys = autoimmune_key, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR")

auto_dis_ids_2 <- MeSHDbi::select(MeSH.AOR.db, keys = auto_dis_ids$OFFSPRING, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR")

auto_dis_ids_3 <- MeSHDbi::select(MeSH.AOR.db, keys = auto_dis_ids_2$OFFSPRING, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR")

auto_dis_ids_4 <- MeSHDbi::select(MeSH.AOR.db, keys = auto_dis_ids_3$OFFSPRING, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR")

auto_dis_ids_5 <- MeSHDbi::select(MeSH.AOR.db, keys = auto_dis_ids_4$OFFSPRING, columns = c("ANCESTOR", "OFFSPRING"), keytype = "ANCESTOR") # 0, so last one to get offspring terms

all_terms <- rbind(auto_dis_ids,auto_dis_ids_2) %>% rbind(., auto_dis_ids_3) %>% rbind(., auto_dis_ids_4)

# add MeSH ID for Chrohn: D003424 and IBD: D015212 since they are autoimmune disorders
#all_terms <- rbind(all_terms, data.frame(ANCESTOR = "D003424", OFFSPRING = "D015212"))

```

```{r}
# Gets names of autoimmune diseases
parent_names <- MeSHDbi::select(MeSH.db, keys = all_terms$ANCESTOR, columns = c("MESHTERM"), keytype = "MESHID")
offspring_names <- MeSHDbi::select(MeSH.db, keys = all_terms$OFFSPRING, columns = c("MESHTERM"), keytype = "MESHID")

# make df of all names of autoimmune diseases
all_terms <- rbind(parent_names, offspring_names) %>% mutate(MESHTERM = tolower(MESHTERM)) %>% unique()

```

```{r}
# Gets synonyms

raw_terms = rbind(parent_names, offspring_names)

# get synonyms
syns <- MeSHDbi::select(MeSH.db, keys = raw_terms$MESHTERM, columns = c("MESHTERM", "SYNONYM"), keytype = "MESHTERM")

all_syns <- syns %>% mutate(MESHTERM = tolower(MESHTERM)) %>% mutate(SYNONYM = tolower(SYNONYM))

syn_df = all_syns$SYNONYM %>% as.data.frame(., stringsAsFactors = F)
syn_list = c()
for(i in seq(1:dim(syn_df)[1])){
 syn_list = c(syn_list, strsplit(syn_df[i,1],  "\\|"))
}

syn_list = unlist(syn_list) %>% unique()

```

```{r}
# Get GDA with autoimmune diseases
# Make a df with Meshterms and their GDA name equivalent
# Made from observation

GDA_disease = c("anemia hemolytic","arthritis juvenile", "rheumatoid arthritis", "autoimmune diseases", "lymphoproliferative syndrome", "encephalomyelitis autoimmune", "giant cell arteritis","glomerulonephritis iga" , "glomerulonephritis membranous", "graves disease", "graves ophthalmopathy", "hashimoto disease", "hepatitis autoimmune", "leukoencephalopathies", "systemic lupus erythematosus", "multiple sclerosis", "myasthenia gravis", "neuromyelitis optica", "sjögren syndrome", "thyroiditis autoimmune", "vasculitis", "inflammatory bowel disease", "crohn disease", "psoriasis")


GDA_auto = GDA_data[GDA_data$DiseaseName %in% GDA_disease, c("hgnc_symbol", "DiseaseName")]
colnames(GDA_auto)[1] <- "Symbol"

```

# Remove root nodes and experimental models from 

remove = c("autoimmune diseases of the nervous system", "demyelinating autoimmune diseases, cns", "nervous system autoimmune disease, experimental", "vasculitis, central nervous system", "anti-neutrophil cytoplasmic antibody-associated vasculitis", "myasthenia gravis, autoimmune, experimental")

```{r}
# https://www.aarda.org/diseaselist/ <- NIH links to this site

aarda_disease_list = c("autoimmune diseases", "esophageal achalasia", "idiopathic achalasia", "agammaglobulinemia", "alopecia", "amyloidosis visceral", "spondylitis ankylosing", "glomerulonephritis", "glomerulonephritis iga", "glomerulonephritis membranous", "encephalomyelitis autoimmune", "hepatitis autoimmune", "autoimmune thyroid disease")

# https://www.autoimmuneinstitute.org/resources/autoimmune-disease-list/

```



# Examining the overlap of gene sets

## Venn Diagrams

# What is the general overlap of genes in our innate and autoimmune diseases data set?
```{r}
# Make a venn diagram to look at the overlap
autos <- GDA_auto$Symbol %>% unique()
innates <- as.character(all_genes_df$Symbol) %>% unique()

euler(list(autoimmuneDiseases = autos, innateImmunity = innates)) %>% plot(., quantities = T)

```

```{r}

hypergeom_test = function(success, universe_success, universe_failure, size_collected){
  phyper(q = success, m = universe_success, n = universe_failure, k = size_collected, lower.tail = TRUE, log.p = FALSE)
}
```


```{r}
# How signif. is this overlap?

genes_i <- autos
genes_j <- innates
all <- unique(c(genes_i, genes_j))
    
universe_success <- intersect(genes_i, genes_j)
q <- length(universe_success) / length(all)
universe_failure <- all[!(all %in% universe_success)]
size_collected <- length(all)
    
hypergeom_test(success = q, universe_success = length(universe_success), universe_failure = length(universe_failure), size_collected = size_collected)

```


# Given our PPI data, how does this overlap change?
```{r}
ppi_auto <- autos[autos %in% V(ppi_g)$name]
ppi_innate = innates[innates %in% V(ppi_g)$name]

euler(list(autoimmuneDiseases = ppi_auto, innateImmunity = ppi_innate)) %>% plot(., quantities = T)

```

```{r}
# How signif. is this overlap?

genes_i <- ppi_auto
genes_j <- ppi_innate
all <- unique(c(genes_i, genes_j))
    
universe_success <- intersect(genes_i, genes_j)
q <- length(universe_success) / length(all)
universe_failure <- all[!(all %in% universe_success)]
size_collected <- length(all)
    
hypergeom_test(q, length(universe_success), length(universe_failure), size_collected)

```





# Do to autoimmune diseases genes form a significant LCC?
```{r}
source("/Users/ursulawidocki/Desktop/BarabasiLab/NetMedTools.R")

LCC_all_auto = LCC_signif(G = ppi_g, targets = ppi_auto, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_all_auto$size, LCC_all_auto$distribution)
hist(LCC_all_auto$distribution, main = "All Autoimmune Diseases LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_all_auto$size, col = "red")
```

```{r}
# Degrees of Genes in LCC and not in LCC

# first make the subgraph
auto_graph <- induced_subgraph(ppi_g, ppi_auto)
temp <- components(auto_graph)$membership 
inLCC_auto = names(temp[temp == 1])
nonLCC_auto = names(temp[temp != 1])

# plot non LCC degrees
not_auto_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_auto)

not_LCC_auto_df <- not_auto_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_auto_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in Autoimmune Diseases LCC") +
  theme_minimal()

# plot LCC degrees
LCC_auto_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_auto) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_auto_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Autoimmune Diseases LCC") +
  theme_minimal()

```

```{r}
# is there one connected component?
components(auto_graph)

```

```{r}
# Check out the innate immunity LCC, just in case
innate_graph <- induced_subgraph(ppi_g, ppi_innate)
temp <- components(innate_graph)$membership
inLCC_innate = names(temp[temp == 1])

LCC_innate = LCC_signif(G = ppi_g, targets = ppi_innate, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_innate$size, LCC_innate$distribution)
hist(LCC_innate$distribution, main = "Innate Immunity LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_innate$size, col = "red")
```




# How do the LCCs of innate immunity and autoimmune disease module overlap?

```{r}
euler(list(autoimmuneDiseaseLCC = inLCC_auto, innateImmunityLCC = inLCC_innate)) %>% plot(., quantities = T)

```

```{r}
genes_i <- inLCC_auto
genes_j <- inLCC_innate
all <- unique(c(genes_i, genes_j))
    
universe_success <- intersect(genes_i, genes_j)
q <- length(universe_success) / length(all)
universe_failure <- all[!(all %in% universe_success)]
size_collected <- length(all)
    
hypergeom_test(q, length(universe_success), length(universe_failure), size_collected)
```

# Does the intersect of Autoimmune Diseases and Innate Immunity form an LCC?
```{r}
# Intersect LCC

genes_intersect = inLCC_auto[inLCC_auto %in% inLCC_innate] # 403
#length(unique(genes_intersect))

LCC_inter = LCC_signif(G = ppi_g, targets = genes_intersect, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_inter$size, LCC_inter$distribution)
hist(LCC_inter$distribution, main = "Intersect of Innate and Autoimmune Disease LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_inter$size, col = "red")

```

```{r}
# Degrees of Genes in LCC and not in LCC

# first make the subgraph
inter_graph <- induced_subgraph(ppi_g, genes_intersect)
temp <- components(inter_graph)$membership 
inLCC_inter = names(temp[temp == 1])
nonLCC_inter = names(temp[temp != 1])

# plot non LCC degrees
not_inter_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_inter)

not_LCC_inter_df <- not_inter_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_inter_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Intersection but Not in Auto-Innate LCC") +
  theme_minimal()

# plot LCC degrees
LCC_inter_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_inter) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_inter_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Intersection of Auto-Innate LCC") +
  theme_minimal()
```
# Enrichment of this Intersection LCC

```{r}
# domain_scope = "custom" or "custom_annotated"
# custom_bg = # parameter for custom background set

query_genes = inLCC_inter
background_genes = unique(GDA_auto$Symbol)

# Uses all databases available: GO, Ensembl, KEGG, and Reactome
# Correction Method: fdr

enrich_inter <- gost(query = query_genes, 
                organism = "hsapiens", ordered_query = FALSE, 
                multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = FALSE, 
                user_threshold = 0.05, correction_method = "fdr", 
                domain_scope = "custom", custom_bg = background_genes, 
                numeric_ns = "", sources = NULL, as_short_link = FALSE)

enrich_inter_df <- enrich_inter$result %>% mutate(term_name = tolower(term_name))

```

```{r}
# Looking through term names

# interferon, cytokines


look_here = enrich_inter_df[!grepl("interferon", enrich_inter_df$term_name),]
look_here = look_here[!grepl("cytokine", look_here$term_name), ]
look_here = look_here[!grepl("inflammatory", look_here$term_name), ]
look_here = look_here[!grepl("adaptive", look_here$term_name), ]
look_here = look_here[!grepl("il-", look_here$term_name), ]
look_here = look_here[!grepl("leukocyte", look_here$term_name), ]
look_here = look_here[!grepl("interleukin", look_here$term_name), ]
look_here = look_here[!grepl("t cell", look_here$term_name), ]
look_here = look_here[!grepl("b cell", look_here$term_name), ]
look_here = look_here[!grepl("lymphocyte", look_here$term_name), ]
look_here = look_here[!grepl("innate", look_here$term_name), ]
look_here = look_here[!grepl("complement", look_here$term_name), ]
look_here = look_here[!grepl("c-type lectin receptor", look_here$term_name), ]
look_here = look_here[!grepl("immune system", look_here$term_name), ]

#
```

```{r}
# Look at intersect LCC gene names

sort(inLCC_inter)

```

```{r}
# Which diseases have genes in the intersect?

inter_autodisease = GDA_auto[GDA_auto$Symbol %in% inLCC_inter, "DiseaseName"] %>% unique()

inter_alldisease = GDA_data[GDA_data$hgnc_symbol %in% inLCC_inter, "DiseaseName"] %>% unique()

```












# Looking at LCCs and separation between disease modules

```{r}
# for each autoimmune disease found in GDA

keep_disease = c()

for(dis in GDA_disease){
  # get genes of disease
  genes_df = subset(GDA_data, GDA_data$DiseaseName == dis)
  genes <- genes_df[!duplicated(genes_df$hgnc_symbol), "hgnc_symbol"]
  genes = genes[genes %in% V(ppi_g)$name]
  
  # assess LCC of disease
  LCC_temp = LCC_signif(G = ppi_g, targets = genes, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)
  if(LCC_temp$p_val < 0.05 & LCC_temp$size > 1){
    print(dis)
    keep_disease = c(keep_disease, dis)
  }

}
  
```

```{r}
# Separation of these diseases and innate immunity

keep_dis = GDA_auto[GDA_auto$DiseaseName %in% keep_disease,]
colnames(keep_dis) = c("Genes", "Label")

# all autoimmunity genes
genes_auto <- GDA_data$hgnc_symbol %>% unique() 
genes_auto = genes_auto[genes_auto %in% V(ppi_g)$name]
auto_df = genes_auto %>% as.data.frame()
auto_df$Label <- "All Auto"
colnames(auto_df)[1] = "Genes"

# all innate immunity genes
genes_all_innate <- all_genes_df$Symbol %>% unique() 
genes_all_innate = genes_all_innate[genes_all_innate %in% V(ppi_g)$name]
all_innate_df = genes_all_innate %>% as.data.frame()
all_innate_df$Label <- "All Innate"
colnames(all_innate_df)[1] = "Genes"

# intersect
inter_labels = inLCC_inter %>% as.data.frame()
inter_labels$Label <- "Intersect"
colnames(inter_labels)[1] = "Genes"

# GO
go_df <- subset(all_genes_df, all_genes_df$GO == "GO.DB")
genes_go <- go_df[!duplicated(go_df$Symbol), "Symbol"] 
genes_go = genes_go[genes_go %in% V(ppi_g)$name]
go_df = genes_go %>% as.data.frame()
go_df$Label <- "GO"
colnames(go_df)[1] = "Genes"

# InnateDB
innate_df <- subset(all_genes_df, all_genes_df$InnateDB == "InnateDB")
genes_innate <- innate_df[!duplicated(innate_df$Symbol), "Symbol"]
genes_innate = genes_innate[genes_innate %in% V(ppi_g)$name]
innate_df = genes_innate %>% as.data.frame()
innate_df$Label <- "InnateDB"
colnames(innate_df)[1] = "Genes"

# KEGG
kegg_df <- subset(all_genes_df, all_genes_df$KEGG == "KEGG.db")
genes_kegg <- kegg_df[!duplicated(kegg_df$Symbol), "Symbol"]
genes_kegg = genes_kegg[genes_kegg %in% V(ppi_g)$name]
kegg_df = genes_kegg %>% as.data.frame()
kegg_df$Label <- "KEGG"
colnames(kegg_df)[1] = "Genes"

# Reactome
reactome_df <- subset(all_genes_df, all_genes_df$ReactomeDB == "ReactomeDB")
genes_reactome <- reactome_df[!duplicated(reactome_df$Symbol), "Symbol"]
genes_reactome = genes_reactome[genes_reactome %in% V(ppi_g)$name]
reactome_df = genes_reactome %>% as.data.frame()
reactome_df$Label <- "Reactome"
colnames(reactome_df)[1] = "Genes"

# Bind the gene and labels together
sep_labels = rbind(keep_dis, auto_df) %>% rbind(., all_innate_df) %>% rbind(., go_df) %>% rbind(., innate_df) %>% rbind(., kegg_df) %>% rbind(., reactome_df) %>% rbind(.,inter_labels)

# Calc. Sep.
all_sep = module_sep(ppi_g, sep_labels)

sab_all = all_sep$Sab
sab_all[is.na(sab_all)] <- 0 # make NA 0
sab_all = sab_all + t(sab_all)

superheat(sab_all, pretty.order.rows = T, pretty.order.cols = T, bottom.label.text.angle = 90, heat.pal = c("blue", "white", "red"), left.label.text.size = 3, bottom.label.text.size = 3, heat.pal.values = c(0, 0.5, 1) )

```

```{r}
# Venn Diagram with 15 significant diseases

euler(list(anemia = GDA_auto[GDA_auto$DiseaseName == "anemia hemolytic", "Symbol"], juvenileArthritis = GDA_auto[GDA_auto$DiseaseName == "arthritis juvenile", "Symbol"], RA = GDA_auto[GDA_auto$DiseaseName == "rheumatoid arthritis", "Symbol"], Other =  GDA_auto[GDA_auto$DiseaseName == "autoimmune diseases", "Symbol"], lymphSyndrome = GDA_auto[GDA_auto$DiseaseName == "lymphoproliferative syndrome", "Symbol"], enceph = GDA_auto[GDA_auto$DiseaseName == "encephalomyelitis autoimmune", "Symbol"], graves = GDA_auto[GDA_auto$DiseaseName == "graves disease", "Symbol"], hep = GDA_auto[GDA_auto$DiseaseName == "hepatitis autoimmune", "Symbol"], leukoenceph = GDA_auto[GDA_auto$DiseaseName == "leukoencephalopathies", "Symbol"], lupus = GDA_auto[GDA_auto$DiseaseName == "systemic lupus erythematosus", "Symbol"], MS = GDA_auto[GDA_auto$DiseaseName == "multiple sclerosis", "Symbol"], myaGravis = GDA_auto[GDA_auto$DiseaseName == "myasthenia gravis", "Symbol"], IBD = GDA_auto[GDA_auto$DiseaseName == "inflammatory bowel disease", "Symbol"], Crohn = GDA_auto[GDA_auto$DiseaseName == "crohn disease", "Symbol"], psoriasis = GDA_auto[GDA_auto$DiseaseName == "psoriasis", "Symbol"], InnateLCC = inLCC_innate)) %>% plot(., quantities = T)


```











##################################################################################################################################################

```{r}
# remove names that are not diseases but category names
remove = c("autoimmune diseases of the nervous system", "demyelinating autoimmune diseases, cns", "nervous system autoimmune disease, experimental", "vasculitis, central nervous system", "anti-neutrophil cytoplasmic antibody-associated vasculitis", "myasthenia gravis, autoimmune, experimental")

all_autodisease_names = all_autodisease_names[!(all_autodisease_names$MESHTERM %in% remove),]

```


# Get genes associated with these autoimmune diseases
```{r}
# Get list of diseases in GDA data
# clean gene names

doesItWork_auto = gsub(pattern = "-", replacement = " ", x = all_autodisease_names$MESHTERM , ignore.case = T)
doesItWork_auto = gsub("[^0-9A-Za-z ]","" , doesItWork_auto,ignore.case = TRUE)
auto_disease_unique = unique(doesItWork_auto)

doesItWork_GDA = gsub(pattern = "-", replacement = " ", x = GDA_data$DiseaseName, ignore.case = T)
doesItWork_GDA = gsub("[^0-9A-Za-z ]","" , doesItWork_GDA, ignore.case = TRUE)
GDA_disease_unique = unique(doesItWork_GDA)

disease_dist = stringdistmatrix(a = auto_disease_unique, b = GDA_disease_unique, method = "cosine")
disease_dist = disease_dist %>% as.data.frame()
rownames(disease_dist) = auto_disease_unique
colnames(disease_dist) = GDA_disease_unique

```

```{r}
# Get disease names in GDA data that are 0.1 away by cosine similarity to MeSH terms

sim_threshold = 0.04 # at 0.01, I get 17 diseases, 0.04 -> 19
keep_disease = c()
for(i in seq(1:ncol(disease_dist))){
  
  dist_vect_temp = disease_dist[,i]
  
  for(j in seq(1:nrow(disease_dist))){
    if(dist_vect_temp[j] <= sim_threshold){
      dis_to_keep =  colnames(disease_dist)[i]
      print(paste0("MeSH: ", rownames(disease_dist)[j],"   GDA Name: ", dis_to_keep))
      keep_disease = c(keep_disease, dis_to_keep)
    }
  }
}

#keep_disease = unique(keep_disease)

```

With 0.05, this is the only error:
"MeSH: caplan syndrome   GDA Name: allanson pantzar mcleod syndrome"
These are two very different diseases.

```{r}
sum(GDA_disease_unique %in% all_autodisease_names$MESHTERM) # there are 8 autoimmune diseases in there, by exact terms
```


## Venn Diagrams

```{r}
# Get genes from GDA associated with diseases 
autoimmune_genes <- GDA_data %>% dplyr::filter(GDA_data$DiseaseName %in% GDA_disease) #
autoimmune_genes$Type <- "Autoimmunity"
colnames(autoimmune_genes)[3] <- c("Symbol")

innateimmune_genes <- as.data.frame(all_genes_df$Symbol) %>% unique()
innateimmune_genes$Type <- "Innate Immunity"
colnames(innateimmune_genes)[1] <-c("Symbol")
```

# What is the general overlap of genes in our innate and autoimmune diseases data set?
```{r}
# Make a venn diagram to look at the overlap
autos <- autoimmune_genes$Symbol %>% unique()
innates <- as.character(innateimmune_genes$Symbol) %>% unique()

venn.diagram(
  x = list(autos, innates),
  category.names = c("Autoimmunity" , "Innate Immunity"),
  filename = 'All_Innate_vs_Auto.png',
  height = 3000, 
  width = 4000,
  output=TRUE,
  main = "Autoimmunity Disease Assoc. Genes with All Innate Immunity"
)
```

```{r}
genes_inter = autos[autos %in% innates]
length(unique(genes_inter))
```






```{r}
# Degrees of Genes in LCC and not in LCC

# first make the subgraph
auto_graph <- induced_subgraph(ppi_g, ppi_auto)
temp <- components(auto_graph)$membership # 
inLCC_auto = names(temp[temp == 1])
nonLCC_auto = names(temp[temp != 1])

# plot non LCC degrees
not_auto_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_auto)

not_LCC_auto_df <- not_auto_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_auto_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in Autoimmune Diseases LCC") +
  theme_minimal()

# plot LCC degrees
LCC_auto_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_auto) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_auto_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Autoimmune Diseases LCC") +
  theme_minimal()

```

```{r}
# Were there other connected components # Yes!
count_df = as.character(components(auto_graph)$csize) %>% as.data.frame()
colnames(count_df)[1] = "Size"

count_df %>% summarise(., count = n(), group_by=Size)

# what us the one high degree gene (degree > 1000) # ETS1
```


# What is the overlap between the innate immunity interactome and the autoimmune disease LCC
```{r}
innate_graph <- induced_subgraph(ppi_g, ppi_innate)
temp <- components(innate_graph)$membership
inLCC_innate = names(temp[temp == 1])

venn.diagram(
  x = list(inLCC_auto, inLCC_innate),
  category.names = c("Autoimmunity LCC" , "Innate Immunity LCC"),
  filename = 'LCC_Innate_vs_Auto.png',
  height = 3000, 
  width = 4000,
  output=TRUE,
  main = "Autoimmunity Disease Assoc. LCC with Innate Immunity LCC"
)

```



## Do the diseases modules form significant ineractomes?

# "arthritis juvenile" LCC
```{r}
arthjuv_df <- subset(GDA_data, GDA_data$DiseaseName == "arthritis juvenile")
genes_arthjuv <- arthjuv_df[!duplicated(arthjuv_df$hgnc_symbol), "hgnc_symbol"]
genes_arthjuv = genes_arthjuv[genes_arthjuv %in% V(ppi_g)$name]

LCC_arth_juv = LCC_signif(G = ppi_g, targets = genes_arthjuv, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_arth_juv$size, LCC_arth_juv$distribution)
hist(LCC_arth_juv$distribution, main = "Juvenile Arthritis LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_arth_juv$size, col = "red")
```

```{r}
# first make the subgraph
ja_graph <- induced_subgraph(ppi_g, genes_arthjuv)
temp <- components(ja_graph)$membership # 
inLCC_ja = names(temp[temp == 2])
nonLCC_ja = names(temp[temp != 2])

# plot non LCC degrees
not_ja_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_ja)

not_LCC_ja_df <- not_ja_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_ja_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in Juvenile Arthritis LCC") +
  theme_minimal()

# plot LCC degrees
LCC_ja_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_ja) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_ja_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Juvenile Arthritis LCC") +
  theme_minimal()

```

# "encephalomyelitis autoimmune" LCC
```{r}
enceph_df <- subset(GDA_data, GDA_data$DiseaseName == "encephalomyelitis autoimmune")
genes_enceph <- enceph_df[!duplicated(enceph_df$hgnc_symbol), "hgnc_symbol"]
genes_enceph = genes_enceph[genes_enceph %in% V(ppi_g)$name]

LCC_enceph = LCC_signif(G = ppi_g, targets = genes_enceph, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_enceph$size, LCC_enceph$distribution)
hist(LCC_enceph$distribution, main = "Encephosmyelitis LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_enceph$size, col = "red")
```

```{r}
enceph_graph <- induced_subgraph(ppi_g, genes_enceph)
temp <- components(enceph_graph)$membership # 
inLCC_enceph = names(temp[temp == 2])
nonLCC_enceph = names(temp[temp != 2])

# plot non LCC degrees
not_enceph_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_enceph)

not_LCC_enceph_df <- not_enceph_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_enceph_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in Enceph. LCC") +
  theme_minimal()

# plot LCC degrees
LCC_enceph_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_enceph) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_enceph_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Enceph. LCC") +
  theme_minimal()

```

# "giant cell arteritis" LCC
```{r}
giant_df <- subset(GDA_data, GDA_data$DiseaseName == "giant cell arteritis")
genes_giant <- giant_df[!duplicated(giant_df$hgnc_symbol), "hgnc_symbol"]
genes_giant = genes_giant[genes_giant %in% V(ppi_g)$name]

LCC_giant = LCC_signif(G = ppi_g, targets = genes_giant, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_giant$size, LCC_giant$distribution)
hist(LCC_giant$distribution, main = "Giant Cell Arteritis LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_giant$size, col = "red")
```

```{r}
giant_graph <- induced_subgraph(ppi_g, genes_giant)
components(giant_graph) # 

# plot LCC degrees
deg_giant_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% genes_giant) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(deg_giant_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Giant Cell Art.") +
  theme_minimal()

```


# "glomerulonephritis iga" LCC
```{r}
iga_df <- subset(GDA_data, GDA_data$DiseaseName == "glomerulonephritis iga")
genes_iga <- iga_df[!duplicated(iga_df$hgnc_symbol), "hgnc_symbol"]
genes_iga = genes_iga[genes_iga %in% V(ppi_g)$name]

LCC_iga = LCC_signif(G = ppi_g, targets = genes_iga, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_iga$size, LCC_iga$distribution)
hist(LCC_iga$distribution, main = "Glomerulonephritis Iga LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_iga$size, col = "red")
```

```{r}
iga_graph <- induced_subgraph(ppi_g, genes_iga)
components(iga_graph) # 

# plot LCC degrees
deg_iga_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% genes_iga) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(deg_iga_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Glom. Iga") +
  theme_minimal()

```

# "glomerulonephritis membranous"
```{r}
glom_df <- subset(GDA_data, GDA_data$DiseaseName == "glomerulonephritis membranous")
genes_glom <- glom_df[!duplicated(glom_df$hgnc_symbol), "hgnc_symbol"]
genes_glom = genes_glom[genes_glom %in% V(ppi_g)$name]

LCC_glom = LCC_signif(G = ppi_g, targets = genes_glom, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_glom$size, LCC_glom$distribution)
hist(LCC_glom$distribution, main = "Glomerulonephritis Membranous LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_glom$size, col = "red")
```

```{r}
glom_graph <- induced_subgraph(ppi_g, genes_glom)
components(glom_graph) 

# plot LCC degrees
deg_glom_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% genes_glom) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(deg_glom_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Glom. Mem.") +
  theme_minimal()

```


# "graves disease" LCC
```{r}
grav_df <- subset(GDA_data, GDA_data$DiseaseName == "graves disease")
genes_grav <- grav_df[!duplicated(grav_df$hgnc_symbol), "hgnc_symbol"]
genes_grav = genes_grav[genes_grav %in% V(ppi_g)$name]

LCC_grav = LCC_signif(G = ppi_g, targets = genes_grav, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_grav$size, LCC_grav$distribution)
hist(LCC_grav$distribution, main = "Graves Disease LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_grav$size, col = "red")
```

```{r}
grav_graph <- induced_subgraph(ppi_g, genes_grav)
temp = components(grav_graph)$membership
inLCC_grav = names(temp[temp == 5])
nonLCC_grav = names(temp[temp != 5])

# plot non LCC degrees
not_grav_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_grav)

not_LCC_grav_df <- not_grav_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_grav_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in Graves Disease LCC") +
  theme_minimal()

# plot LCC degrees
LCC_grav_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_grav) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_grav_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Graves Disease LCC") +
  theme_minimal()
```


# "graves ophthalmopathy" LCC
```{r}
gravop_df <- subset(GDA_data, GDA_data$DiseaseName == "graves ophthalmopathy")
genes_gravop <- gravop_df[!duplicated(gravop_df$hgnc_symbol), "hgnc_symbol"]
genes_gravop = genes_gravop[genes_gravop %in% V(ppi_g)$name]

LCC_gravop = LCC_signif(G = ppi_g, targets = genes_gravop, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_gravop$size, LCC_gravop$distribution)
hist(LCC_iga$distribution, main = "Graves Ophthalmopathy LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_gravop$size, col = "red")
```

```{r}
# plot LCC degrees
deg_gravop_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% genes_gravop) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(deg_gravop_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Graves Ophthalmopathy") +
  theme_minimal()
```

"hashimoto disease" LCC
```{r}
hash_df <- subset(GDA_data, GDA_data$DiseaseName == "hashimoto disease")
genes_hash <- hash_df[!duplicated(hash_df$hgnc_symbol), "hgnc_symbol"]
genes_hash = genes_hash[genes_hash %in% V(ppi_g)$name]

LCC_hash = LCC_signif(G = ppi_g, targets = genes_hash, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_hash$size, LCC_hash$distribution)
hist(LCC_hash$distribution, main = "Hashimoto Disease LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_hash$size, col = "red")
```

```{r}
# plot LCC degrees
deg_hash_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% genes_hash) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(deg_hash_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Hashimoto") +
  theme_minimal()
```

# "hepatitis autoimmune" LCC
```{r}
hep_df <- subset(GDA_data, GDA_data$DiseaseName == "hepatitis autoimmune")
genes_hep <- hep_df[!duplicated(hep_df$hgnc_symbol), "hgnc_symbol"]
genes_hep = genes_hep[genes_hep %in% V(ppi_g)$name]

LCC_hep = LCC_signif(G = ppi_g, targets = genes_hep, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_hep$size, LCC_hep$distribution)
hist(LCC_hep$distribution, main = "Hepatitis Autoimmune LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_hep$size, col = "red")
```

```{r}
hep_graph <- induced_subgraph(ppi_g, genes_hep)
temp = components(hep_graph)$membership
inLCC_hep = names(temp[temp == 4])
nonLCC_hep = names(temp[temp != 4])

# plot non LCC degrees
not_hep_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_hep)

not_LCC_hep_df <- not_hep_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_hep_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in Hep. LCC") +
  theme_minimal()

# plot LCC degrees
LCC_hep_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_hep) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_hep_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Hep. LCC") +
  theme_minimal()
```


# "multiple sclerosis" LCC
```{r}
ms_df <- subset(GDA_data, GDA_data$DiseaseName == "multiple sclerosis")
genes_ms <- ms_df[!duplicated(ms_df$hgnc_symbol), "hgnc_symbol"]
genes_ms = genes_ms[genes_ms %in% V(ppi_g)$name]

LCC_ms = LCC_signif(G = ppi_g, targets = genes_ms, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_ms$size, LCC_ms$distribution)
hist(LCC_ms$distribution, main = "Multiple Sclerosis LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_ms$size, col = "red")
```

```{r}
ms_graph <- induced_subgraph(ppi_g, genes_ms)
temp = components(ms_graph)$membership
inLCC_ms = names(temp[temp == 1])
nonLCC_ms = names(temp[temp != 1])

# plot non LCC degrees
not_ms_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_ms)

not_LCC_ms_df <- not_ms_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_ms_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in MS LCC") +
  theme_minimal()

# plot LCC degrees
LCC_ms_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_ms) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_ms_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in MS LCC") +
  theme_minimal()
```


# "myasthenia gravis" LCC
```{r}
mya_df <- subset(GDA_data, GDA_data$DiseaseName == "myasthenia gravis")
genes_mya <- mya_df[!duplicated(mya_df$hgnc_symbol), "hgnc_symbol"]
genes_mya = genes_mya[genes_mya %in% V(ppi_g)$name]

LCC_mya = LCC_signif(G = ppi_g, targets = genes_mya, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_mya$size, LCC_mya$distribution)
hist(LCC_mya$distribution, main = "Myasthenia Gravis LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 800), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_mya$size, col = "red")
```

```{r}
mya_graph <- induced_subgraph(ppi_g, genes_mya)
temp = components(mya_graph)$membership
inLCC_mya = names(temp[temp == 4])
nonLCC_mya = names(temp[temp != 4])

# plot non LCC degrees
not_mya_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_mya)

not_LCC_mya_df <- not_mya_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_mya_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in Mya. Gravis LCC") +
  theme_minimal()

# plot LCC degrees
LCC_mya_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_mya) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_mya_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Mya. Gravis LCC") +
  theme_minimal()
```


# "neuromyelitis optica" LCC
```{r}
neuro_df <- subset(GDA_data, GDA_data$DiseaseName == "neuromyelitis optica")
genes_neuro <- neuro_df[!duplicated(neuro_df$hgnc_symbol), "hgnc_symbol"]
genes_neuro = genes_neuro[genes_neuro %in% V(ppi_g)$name]

LCC_neuro = LCC_signif(G = ppi_g, targets = genes_neuro, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_neuro$size, LCC_neuro$distribution)
hist(LCC_neuro$distribution, main = "Neuromyelitis Optica LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_neuro$size, col = "red")
```

```{r}
# plot LCC degrees
deg_neuro_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% genes_neuro) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(deg_neuro_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Neuro. Optica") +
  theme_minimal()
```

# "rheumatoid arthritis" LCC
```{r}
ra_df <- subset(GDA_data, GDA_data$DiseaseName == "rheumatoid arthritis")
genes_ra <- ra_df[!duplicated(ra_df$hgnc_symbol), "hgnc_symbol"]
genes_ra = genes_ra[genes_ra %in% V(ppi_g)$name]

LCC_ra = LCC_signif(G = ppi_g, targets = genes_ra, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_ra$size, LCC_ra$distribution)
hist(LCC_ra$distribution, main = "Rheumatoid Arthritis LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_ra$size, col = "red")
```

```{r}
ra_graph <- induced_subgraph(ppi_g, genes_ra)
temp = components(ra_graph)$membership
inLCC_ra = names(temp[temp == 2])
nonLCC_ra = names(temp[temp != 2])

# plot non LCC degrees
not_ra_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_ra)

not_LCC_ra_df <- not_ra_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_ra_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in RA LCC") +
  theme_minimal()

# plot LCC degrees
LCC_ra_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_ra) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_ra_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in RA LCC") +
  theme_minimal()
```



# "systemic lupus erythematosus"
```{r}
lup_df <- subset(GDA_data, GDA_data$DiseaseName == "systemic lupus erythematosus")
genes_lup <- lup_df[!duplicated(lup_df$hgnc_symbol), "hgnc_symbol"]
genes_lup = genes_lup[genes_lup %in% V(ppi_g)$name]

LCC_lup = LCC_signif(G = ppi_g, targets = genes_lup, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_lup$size, LCC_lup$distribution)
hist(LCC_lup$distribution, main = "Systemic Lupus Erythematosus LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_lup$size, col = "red")
```

```{r}
lup_graph <- induced_subgraph(ppi_g, genes_lup)
temp = components(lup_graph)$membership
inLCC_lup = names(temp[temp == 1])
nonLCC_lup = names(temp[temp != 1])

# plot non LCC degrees
not_lup_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_lup)

not_LCC_lup_df <- not_lup_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_lup_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in Lupus LCC") +
  theme_minimal()

# plot LCC degrees
LCC_lup_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_lup) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_lup_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Lupus LCC") +
  theme_minimal()
```


# "thyroiditis autoimmune"
```{r}
thy_df <- subset(GDA_data, GDA_data$DiseaseName == "thyroiditis autoimmune")
genes_thy <- thy_df[!duplicated(thy_df$hgnc_symbol), "hgnc_symbol"]
genes_thy = genes_thy[genes_thy %in% V(ppi_g)$name]

LCC_thy = LCC_signif(G = ppi_g, targets = genes_thy, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_thy$size, LCC_thy$distribution)
hist(LCC_thy$distribution, main = "Thyroiditis LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 600), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_thy$size, col = "red")
```

```{r}
# plot LCC degrees
deg_thy_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% genes_thy) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(deg_thy_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Thyroiditis") +
  theme_minimal()
```


# "autoimmune diseases" LCC (the "other" classification)
```{r}
other_df <- subset(GDA_data, GDA_data$DiseaseName == "autoimmune diseases")
genes_other <- other_df[!duplicated(other_df$hgnc_symbol), "hgnc_symbol"]
genes_other = genes_other[genes_other %in% V(ppi_g)$name]

LCC_other = LCC_signif(G = ppi_g, targets = genes_other, num_bins_degree_G = 50, min_bin_degree = 20, iter = 1000)

## Plotting
lim = c(LCC_other$size, LCC_other$distribution)
hist(LCC_other$distribution, main = "Other Autoimmune Diseases LCC Empirical Distribution", xlim = c(min(lim - 50), max(lim + 50)), ylim = c(0, 300), col = 'gray75', ylab = "", breaks = 20)

abline(v = LCC_other$size, col = "red")
```

```{r}
# first make the subgraph
other_graph <- induced_subgraph(ppi_g, genes_other)
temp <- components(other_graph)$membership 
inLCC_other = names(temp[temp == 1])
nonLCC_other = names(temp[temp != 1])

# plot non LCC degrees
not_other_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% nonLCC_other)

not_LCC_other_df <- not_other_df %>%
  group_by(Degree) %>%
  summarise(n = n())

# Plot degree frequency
ggplot(not_LCC_other_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#1f9e89") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes Not in Other Diseases LCC") +
  theme_minimal()

# plot LCC degrees
LCC_other_df <- subset(ppi_degree_df, rownames(ppi_degree_df) %in% inLCC_other) %>%
  group_by(Degree) %>%
  summarize(n = n())

# Plot degrees of nodes in PPI
ggplot(LCC_other_df) +
  aes(x = Degree, y = n) +
  geom_point(size = 1L, colour = "#bd3786") +
  scale_x_continuous(trans = "log10") +
  scale_y_continuous(trans = "log10") +
  labs(x = "Degree", y = "Freq.", title = "Degrees of Nodes in Other Diseases LCC") +
  theme_minimal()
```


# Separation between all 16 diseases and databases of the innate immune system
```{r}
# genes_arthjuv
ja_df = genes_arthjuv %>% as.data.frame()
ja_df$Label <- "Juvenile Arthritis"
colnames(ja_df)[1] = "Genes"
# genes_enceph
enceph_df = genes_enceph %>% as.data.frame()
enceph_df$Label <- "Encephosmyelitis"
colnames(enceph_df)[1] = "Genes"
# genes_giant
giant_df = genes_giant %>% as.data.frame()
giant_df$Label <- "Giant Cell Arteritis"
colnames(giant_df)[1] = "Genes"
# genes_iga
iga_df = genes_iga %>% as.data.frame()
iga_df$Label <- "Glom. Iga"
colnames(iga_df)[1] = "Genes"
# genes_glom
glom_df = genes_glom %>% as.data.frame()
glom_df$Label <- "Glom. Mem."
colnames(glom_df)[1] = "Genes"
# genes_grav
grav_df = genes_grav %>% as.data.frame()
grav_df$Label <- "Graves"
colnames(grav_df)[1] = "Genes"
# genes_gravop
gravop_df = genes_gravop %>% as.data.frame()
gravop_df$Label <- "Graves Ophth."
colnames(gravop_df)[1] = "Genes"
# genes_hash
hash_df = genes_hash %>% as.data.frame()
hash_df$Label <- "Hashimoto"
colnames(hash_df)[1] = "Genes"
# genes_hep
hep_df = genes_hep %>% as.data.frame()
hep_df$Label <- "Hepatitis"
colnames(hep_df)[1] = "Genes"
# genes_ms
ms_df = genes_ms %>% as.data.frame()
ms_df$Label <- "MS"
colnames(ms_df)[1] = "Genes"
# genes_mya
mya_df = genes_mya %>% as.data.frame()
mya_df$Label <- "Mya. Gravis"
colnames(mya_df)[1] = "Genes"
# genes_neuro
neuro_df = genes_neuro %>% as.data.frame()
neuro_df$Label <- "Neuro. Opt."
colnames(neuro_df)[1] = "Genes"
# genes_ra
ra_df = genes_ra %>% as.data.frame()
ra_df$Label <- "RA"
colnames(ra_df)[1] = "Genes"
# genes_lup
lup_df = genes_lup %>% as.data.frame()
lup_df$Label <- "Lupus"
colnames(lup_df)[1] = "Genes"
# genes_thy
thy_df = genes_thy %>% as.data.frame()
thy_df$Label <- "Thyroiditis"
colnames(thy_df)[1] = "Genes"
# genes_other
other_df = genes_other %>% as.data.frame()
other_df$Label <- "Other"
colnames(other_df)[1] = "Genes"
# ppi_auto
ppi_auto_df = ppi_auto %>% as.data.frame()
ppi_auto_df$Label <- "Autoimmune Disease"
colnames(ppi_auto_df)[1] = "Genes"
# ppi_innate
ppi_innate_df = ppi_innate %>% as.data.frame()
ppi_innate_df$Label <- "Innate Immunity"
colnames(ppi_innate_df)[1] = "Genes"

go_df <- subset(all_genes_df, all_genes_df$GO == "GO.DB")
genes_go <- go_df[!duplicated(go_df$Symbol), "Symbol"] 
genes_go = genes_go[genes_go %in% V(ppi_g)$name]
go_df = genes_go %>% as.data.frame()
go_df$Label <- "GO"
colnames(go_df)[1] = "Genes"

innate_df <- subset(all_genes_df, all_genes_df$InnateDB == "InnateDB")
genes_innate <- innate_df[!duplicated(innate_df$Symbol), "Symbol"]
genes_innate = genes_innate[genes_innate %in% V(ppi_g)$name]
innate_df = genes_innate %>% as.data.frame()
innate_df$Label <- "InnateDB"
colnames(innate_df)[1] = "Genes"

kegg_df <- subset(all_genes_df, all_genes_df$KEGG == "KEGG.db")
genes_kegg <- kegg_df[!duplicated(kegg_df$Symbol), "Symbol"]
genes_kegg = genes_kegg[genes_kegg %in% V(ppi_g)$name]
kegg_df = genes_kegg %>% as.data.frame()
kegg_df$Label <- "KEGG"
colnames(kegg_df)[1] = "Genes"

reactome_df <- subset(all_genes_df, all_genes_df$ReactomeDB == "ReactomeDB")
genes_reactome <- reactome_df[!duplicated(reactome_df$Symbol), "Symbol"]
genes_reactome = genes_reactome[genes_reactome %in% V(ppi_g)$name]
reactome_df = genes_reactome %>% as.data.frame()
reactome_df$Label <- "Reactome"
colnames(reactome_df)[1] = "Genes"

# Bind the gene and labels together
sep_labels = rbind(ja_df, enceph_df) %>% rbind(., giant_df) %>% rbind(., iga_df) %>% rbind(., glom_df)
sep_labels = rbind(sep_labels, grav_df) %>% rbind(., gravop_df) %>% rbind(., hash_df) %>% rbind(., hep_df)
sep_labels = rbind(sep_labels, ms_df) %>% rbind(., mya_df) %>% rbind(., neuro_df) %>% rbind(., ra_df)
sep_labels = rbind(sep_labels, lup_df) %>% rbind(., thy_df) %>% rbind(., other_df) %>% rbind(., go_df)
sep_labels = rbind(sep_labels, innate_df) %>% rbind(., kegg_df) %>% rbind(., reactome_df) %>% rbind(., ppi_auto_df)  %>%                   rbind(., ppi_innate_df)

# Calc. Sep.
all_sep = module_sep(ppi_g, sep_labels)

sab_all = all_sep$Sab
sab_all[is.na(sab_all)] <- 0 # make NA 0
sab_all = sab_all + t(sab_all)

superheat(sab_all, pretty.order.rows = T, pretty.order.cols = T)

```


# Code I didn't use

# Use Word2Vec in order to see which disease names are closest to each other using cosine similarity

#```{r}

edit_GDA = gsub(pattern = "-", replacement = " ", x = GDA_data$DiseaseName, ignore.case = T)
edit_GDA = gsub("[^0-9A-Za-z ]","" , edit_GDA, ignore.case = TRUE)
bank_GDA = unique(edit_GDA)

bank_ncbi = c(syn_list, all_terms) %>% unlist() %>% unique() %>% as.data.frame(., stringsAsFactors = F) 
colnames(bank_ncbi) = "Names"
ncbi_bank = bank_ncbi %>% mutate(Names = tolower(Names))
edit_ncbi = gsub(pattern = "-", replacement = " ", x = bank_ncbi$Names, ignore.case = T)
edit_ncbi = gsub("[^0-9A-Za-z ]","" , edit_ncbi, ignore.case = TRUE)
bank_ncbi = unique(edit_ncbi)

# make as one list
all_diseases = c(bank_GDA, bank_ncbi) %>% unique()

# make into file
write.table(all_diseases,"all_disease_list.csv",sep=",")
#```

#```{r} 
require(magrittr)
require(word2vec)

DiseaseNames_w2v = read.table("/Users/ursulawidocki/Desktop/BarabasiLab/Auto_Innate_GDA/all_disease_list.csv" , sep = ",", header = T, stringsAsFactors = F)
colnames(DiseaseNames_w2v) <- "DiseaseName"
model <- read.word2vec( "/Users/ursulawidocki/Desktop/BarabasiLab/Data/pubmed2018_w2v_400D/pubmed2018_w2v_400D.bin" )
terms <- summary(model, "vocabulary")
embedding <- as.matrix(model) #%>% as.data.frame()
Dis = DiseaseNames_w2v$DiseaseName %>% unique()

emb = list()
pb <- txtProgressBar(min = 0, max = length(Dis), style = 3)

average_dis = function(disease, e = embedding2){
  require(magrittr)
  
  t = rownames(e)
  dis = disease %>% 
    stringr::str_split(., " ", simplify = TRUE) %>% 
    as.character()
  
  t_in_dis = sum(t %in% dis)
  if(t_in_dis > 0){
    v =  e[t %in% dis,] %>% 
      matrix(., ncol = ncol(e)) %>% 
      colMeans(., na.rm = TRUE) %>% 
      as.data.frame()
    names(v)= disease
    return(v)
  }
}

lalala = Dis %>% strsplit(., " ") %>% unlist() %>% unique()
embedding2 = embedding[rownames(embedding) %in% lalala, ]

average_dis(disease = Dis[1000], e = embedding2)

require(parallel)
cl = parallel::makePSOCKcluster(10)
clusterExport(cl, "average_dis")
clusterExport(cl, "embedding2")

U = clusterApplyLB(cl, Dis, average_dis)
U %<>% dplyr::bind_cols()

stopCluster(cl)


c = U %>%t%>% na.exclude() %>%  philentropy::distance(., method = "cosine") # matrix with distance between diseases
xxx = U %>%t%>% na.exclude() %>% row.names()
colnames(c) = row.names(c) = xxx
# 
data.table::fwrite(c, "/Users/ursulawidocki/Desktop/BarabasiLab/Data/disease_name_dist.txt")

#```

#```{r}
# from c, keep row from MeSH terms and synonyms
name_dist_matrix = c[which(rownames(c) %in% bank_ncbi),]

potential_names_GDA = c()

for(i in seq(1:dim(name_dist_matrix)[1])){
#for(i in seq(1:40)){
  for(j in seq(1:dim(name_dist_matrix)[2])){
  #for(j in seq(i+1:41)){
   
    if(name_dist_matrix[i,j] >= 0.99){
      #print(paste0("Row: ",  rownames(name_dist_matrix)[i], " Col: ",  colnames(name_dist_matrix)[j]))
      if(colnames(name_dist_matrix)[j] %in% bank_GDA){
        #print(colnames(name_dist_matrix)[j])
        potential_names_GDA = c(potential_names_GDA, colnames(name_dist_matrix)[j])
        print(paste0("Row: ",  rownames(name_dist_matrix)[i], " Col: ",  colnames(name_dist_matrix)[j]))
      }
    }
    
  }
}

length(unique(potential_names_GDA))

#```



